---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# eatPlot

<!-- badges: start -->
[![R-CMD-check](https://github.com/nickhaf/eatPlot/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/nickhaf/eatPlot/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/nickhaf/eatPlot/branch/main/graph/badge.svg)](https://app.codecov.io/gh/nickhaf/eatPlot?branch=main)
<!-- badges: end -->

The goal of eatPlot is to easily plot results stemming from the eatRep package. 

## Installation

You can install the development version of eatPlot from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nickhaf/eatPlot")
```

## Basic workflow
### Data preperation
`eatPlot` makes it simple to prepare `eatRep` output for plotting. Depending on whether you want to plot cross-sectional data or trenddata, you can use either:
```{r}
library(eatPlot)
barplot_data <- prep_no_trend(
  dat = adjusted_means,
  grouping_var = "adjust",
  columns = "adjust",
  competence = "GL",
  sig_niveau = 0.05
)
```

or:
```{r}
lineplot_data <- prep_trend(dat = trend_books, 
                            grouping_var = "KBuecher_imp3", 
                            competence = "GL", 
                            sig_niveau = 0.05)
```
You can also remove specific states, if you don't want to plot them:
```{r}
lineplot_data <- filter_rows(lineplot_data, state = "wholeGroup", remove = TRUE)
```


### Plotting
The prepared data can then fed into one of the plotting functions. For example, if you want to plot a barplot with an ajacent table, first plot both plots indidually, and then merge them together:
```{r}
p_table <- plot_table(barplot_data[["plot_table"]])
p_bar <- plot_bar(barplot_data)

plot_table_bar(p_table, p_bar)
```

Or, if you want a lineplot:
```{r}
p_line <- plot_lineplot(lineplot_data, axis_x_label_centralize = 0.15)
p_line
```

The plots are optimally adjusted for A4-pages, and can be saved as pdf as follows:
```{r}
save_plot(p_line, filename = "../lineplot.pdf")
```



