---
title: "BT 22 example plots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bt22_plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

ACHTUNG: Schaut bitte selbst noch einmal genau, welche Spalten ihr zum Plotten benötigt. Die Plots sind zur Veranschaulichung des Workflows gedacht, es kann sein, dass ihr für bestimmte Kapitel andere Spalten angeben müsst! Also vergleicht am besten noch einmal Stichprobenartig mit dem `eatRep` output, dass es sich um die richtigen Werte handelt.

```{r setup}
library(eatPlot)
```

# Lineplots
## Chapter 4
### Kompetenzwerte Bundesländer
```{r chpt4_line}
## Prepare the data with 'KBuecher_imp3' as grouping_var
plot_dat <- prep_plot(
  dat = trend_books,
  comparisons = "crossDiff", # filter the needed comparisons to reduce ouput
  competence = "GL",
  grouping_vars = "KBuecher_imp3",
  grouping_vars_groups = c("0", "1")
)

## Remove wholeGroup, as we don't want to plot it
plot_dat <- filter_rows(plot_dat,
  column_name = "state_var",
  subsetter = "wholeGroup",
  remove = TRUE
)

p_line_states <- plot_lineplot(
  plot_dat = plot_dat,
  title_superscripts = list("Land-17" = "a",
                           "Land-45" = "3"),
  years_lines = list(c(2011, 2016), c(2016, 2021)),
  years_braces = list(c(2011, 2016), c(2016, 2021)),
  plot_settings = plotsettings_lineplot(default_list = lineplot_4x4)
)

p_line_states
```

```{r, eval = FALSE}
save_plot(p_line_states, filename = "../split_lineplot_2_books-v04.pdf")
```


### Kompetenzwerte Deutschland
```{r chpt_4_ger}
## First we extract the wanted competence areas from the data:
plot_dat_kb <- trend_books[trend_books$kb %in% c("DHW", "GL", "GM", "hoeren", "lesen"), ]

## We can change the order by converting 'kb' into a factor and ordering the levels:
plot_dat_kb$kb <- factor(plot_dat_kb$kb, levels = c("hoeren", "lesen", "GL", "DHW","GM") )

## Than we can prepare it with the according function:
plot_dat_test <- prep_plot(
  dat = plot_dat_kb,
  grouping_vars = "KBuecher_imp3",
  grouping_vars_groups = c("0", "1", "0.vs.1"),
  states = "wholeGroup"
)

## Here we change the seperate_plot_var - Argument to "competence_var", so the different competences are depicted in the tiles:
p_line_ger <- plot_lineplot(
  plot_dat = plot_dat_test,
  seperate_plot_var = "competence_var",
  label_sig_high = NULL,
  years_lines = list(c(2011, 2016), c(2016, 2021)),
  years_braces = list(c(2011, 2016), c(2016, 2021)),
  background_lines = FALSE,
  plot_settings = plotsettings_lineplot(
    default_list = lineplot_2x3
  )
)

p_line_ger
```

```{r, eval = FALSE}
## We dont't want a whole A4 page for this plot, but maybe the half:
save_plot(p_line_ger,
  filename = "../adjusted_means_ger-v02.pdf",
  height = 226.2 / 2 + 10
)
```


# Tables/Barplots
## Chapter 3
### Mindeststandards
```{r chpt_3_MinStand}
dat_bar <- prep_plot(min_stand,
  competence = "lesen",
  parameter = "1"
)[["plot_tablebar"]]

## Some columns have to be prepared manually (with convenience functions):
## wholeGroup should not be plotted in bold, so set to FALSE
dat_bar[dat_bar$state_var == "wholeGroup", grep("sig_", colnames(dat_bar))] <- FALSE

dat_bar <- construct_percent(dat_bar, columns = colnames(dat_bar)[grep("est", colnames(dat_bar))])
for (i in c("2011", "2016", "2021")) {
  dat_bar <- construct_directional_sig(dat_bar, est_column = paste0("est_noTrend_Comp_crossDiff_wholeGroup_", i), sig_column = paste0("sig_noTrend_Comp_crossDiff_wholeGroup_", i))
}

dat_bar$state_var <- gsub("wholeGroup", "Deutschland", dat_bar$state_var)
dat_bar$state_var <- gsub("-", "\uad", dat_bar$state_var)

# Plot 1 ------------------------------------------------------------------
dat_bar_1 <- subset(dat_bar, depVar == "minVerfehlt")

p_bar_1 <- plot_tablebar(
  dat = dat_bar_1,
  bar_label = "est_noTrend_noComp_2021_percent",
  bar_label_sig = "sig_noTrend_Comp_crossDiff_wholeGroup_2021",
  bar_sig = "sig_noTrend_Comp_crossDiff_wholeGroup_2021_directional_sig",
  headers = list("**Land**", "**Mindeststandard nicht erreicht**"),
  columns_table = list("state_var"),
  bar_est = "est_noTrend_noComp_2021_percent",
  y_axis = "state_var",
  plot_settings = plotsettings_tablebarplot(
    axis_x_lims = c(0, 42), # Set a bit higher, so the last number isn't cut off.
    bar_fill_colour = grDevices::rgb(49, 133, 156, maxColorValue = 255),
    columns_alignment = 0,
    columns_width = c(0.45, 0.55),
    headers_alignment = c(0, 0),
    default_list = barplot_plot_frame
  )
)


# Plot 2 ------------------------------------------------------------------

dat_bar_2 <- subset(dat_bar, depVar == "regErreicht")

p_bar_2 <- plot_tablebar(
  dat = dat_bar_2,
  bar_label = "est_noTrend_noComp_2021_percent",
  bar_label_sig = "sig_noTrend_Comp_crossDiff_wholeGroup_2021",
  bar_sig = "sig_noTrend_Comp_crossDiff_wholeGroup_2021_directional_sig",
  bar_est = "est_noTrend_noComp_2021_percent",
  headers = list("**Regelstandard erreicht <br> oder übertroffen**"),
  y_axis = "state_var",
  plot_settings = plotsettings_tablebarplot(
    columns_alignment = 0,
    headers_alignment = 0,
    axis_x_lims = c(0, 72),
    bar_fill_colour = grDevices::rgb(75, 172, 198, maxColorValue = 255),
    default_list = barplot_plot_frame
  )
)



# Plot 3 ------------------------------------------------------------------
dat_bar_3 <- subset(dat_bar, depVar == "optErreicht")

p_bar_3 <- plot_tablebar(
  dat = dat_bar_3,
  bar_label = "est_noTrend_noComp_2021_percent",
  bar_label_sig = "sig_noTrend_Comp_crossDiff_wholeGroup_2021",
  bar_sig = "sig_noTrend_Comp_crossDiff_wholeGroup_2021_directional_sig",
  bar_est = "est_noTrend_noComp_2021_percent",
  headers = list("**Optimalstandard<br>erreicht**"),
  y_axis = "state_var",
  plot_settings = plotsettings_tablebarplot(
    axis_x_lims = c(0, 25),
    headers_alignment = 0,
    default_list = barplot_plot_frame
  )
)

# Combine plots --------------
minsta_plot <- combine_plots(list(p_bar_1, p_bar_2, p_bar_3))

minsta_plot
```

```{r, eval = FALSE}
save_plot(minsta_plot, filename = "../Kap_3_MinSta.pdf", height = 226.2 / 3)
```

### Mindeststandards Trend
```{r chpt_3_MinStand_trend}
dat_bar <- prep_plot(min_stand,
  competence = "lesen",
  parameter = "1"
)[["plot_tablebar"]]


dat_bar <- construct_percent(dat_bar, columns = colnames(dat_bar)[grep("est_|se_", colnames(dat_bar))])

dat_bar$depVar <- gsub("minVerfehlt", "Mindeststandard nicht erreicht (MSA)", dat_bar$depVar)
dat_bar$depVar <- gsub("regErreicht", "Regelstandard erreicht (MSA)", dat_bar$depVar)
dat_bar$depVar <- gsub("optErreicht", "Optimalstandard erreicht (MSA)", dat_bar$depVar)

## Order the data.frame:
dat_bar$y_axis_new <- paste0(dat_bar$state_var, dat_bar$depVar)
## Dummy-variable needed for sorting:
dat_bar$depVar_fac <- factor(dat_bar$depVar, levels = c(
  "Mindeststandard nicht erreicht (MSA)",
  "Regelstandard erreicht (MSA)",
  "Optimalstandard erreicht (MSA)"
))
dat_bar <- dat_bar[order(dat_bar$state_var, dat_bar$depVar_fac), ]

## add a linebreak at the '-':
dat_bar$state_var <- gsub("-", "-<br>", dat_bar$state_var)

# Plot 1 ------------------------------------------------------------------
## Only plot the first state respectively:
dat_bar$state_var[duplicated(dat_bar$state_var)] <- " "


p_bar_1 <- plot_tablebar(
  dat = dat_bar,
  bar_est = "est_Trend_noComp_20112016_percent",
  bar_label = NULL,
  bar_sig = "sig_Trend_noComp_20112016",
  bar_fill = "depVar",
  headers = list("**Land**", " ", "**%**", "**%**", "**%**", "*(SE)*", " "),
  column_spanners = list(
    "**2011**<sup>a<sup>" = 3,
    "**2016**<sup>a<sup>" = 4,
    "**Differenz 2016 - 2011**<sup>a<sup>" = c(5, 7)
  ),
  columns_table = list(
    "state_var",
    "depVar",
    "est_noTrend_noComp_2011_percent",
    "est_noTrend_noComp_2016_percent",
    "est_Trend_noComp_20112016_percent",
    "se_Trend_noComp_20112016_percent"
  ),
  columns_round = list(NULL, NULL, 1, 1, 1, NULL),
  columns_table_se = list(NULL, NULL, NULL, NULL, NULL, "se_Trend_noComp_20112016_percent"),
  columns_table_sig_bold = list(
    NULL, NULL, NULL, NULL, "sig_Trend_noComp_20112016", NULL),
  columns_table_sig_high = list(
    NULL, NULL, NULL, NULL, "sig_Trend_Comp_crossDiff_wholeGroup_20112016", NULL),
  y_axis = "y_axis_new",
  plot_settings = plotsettings_tablebarplot(
    axis_x_lims = c(-20, 20),
    columns_alignment = c(0, 0, 2, 2, 2, 2),
    headers_alignment = c(0, 0, 0.5, 0.5, 0.5, 0.5, 0),
    columns_width = c(0.15, 0.375, 0.07, 0.07, 0.07, 0.07, 0.225),
    default_list = barplot_table_plot_pattern
  )
)


# Plot 2 ------------------------------------------------------------------
p_bar_2 <- plot_tablebar(
  dat = dat_bar,
  bar_est = "est_Trend_noComp_20162021_percent",
  bar_label = NULL,
  bar_sig = "sig_Trend_noComp_20162021",
  bar_fill = "depVar",
  headers = list("**%**", "**%**", "**%**", "*(SE)*", " "),
  column_spanners = list(
    "**2016**" = 1,
    "**2021**" = 2,
    "**Differenz 2021 - 2016**" = c(3, 5)
  ),
  columns_round = list(1, 1, 1, NULL),
  columns_table = list(
    "est_noTrend_noComp_2016_percent",
    "est_noTrend_noComp_2021_percent",
    "est_Trend_noComp_20162021_percent",
    "se_Trend_noComp_20162021_percent"
  ),
  columns_table_se = list(NULL, NULL, NULL, "se_Trend_noComp_20162021_percent"), 
  columns_table_sig_bold = list(
    NULL,
    NULL,
    "sig_Trend_noComp_20162021",
    NULL
  ),
  columns_table_sig_high = list(
    NULL,
    NULL,
    "sig_Trend_Comp_crossDiff_wholeGroup_20162021",
    NULL
  ),
  y_axis = "y_axis_new",
  plot_settings = plotsettings_tablebarplot(
    columns_alignment = c(2, 2, 2, 2),
    columns_width = c(0.13, 0.13, 0.13, 0.13, 0.46),
    headers_alignment = 0.5,
    bar_pattern_spacing = 0.0125,
    default_list = barplot_table_plot_pattern
  )
)

minsta_plot_trend <- combine_plots(list(p_bar_1, p_bar_2))
minsta_plot_trend
```

```{r, eval = FALSE}
save_plot(minsta_plot_trend, filename = "../Kap3_2021_MSA_trend-v04.pdf")
```


### Mindeststandards Frz
```{r chpt_2_frz}
dat_bar <- prep_plot(min_stand,
  competence = "lesen",
  parameter = "1"
)[["plot_tablebar"]]

## Add a second group for illustration (not necessary for real data of course):
dat_bar_2 <- dat_bar
dat_bar_2$grouping_var <- rep("Gymnasium", nrow(dat_bar_2))
dat_bar <- rbind(dat_bar, dat_bar_2)

## Prepare data.frame:
dat_bar <- construct_percent(dat_bar, columns = colnames(dat_bar)[grep("est_|se_", colnames(dat_bar))])
dat_bar$depVar <- gsub("minVerfehlt", "Mindeststandard nicht erreicht (MSA)", dat_bar$depVar)
dat_bar$depVar <- gsub("regErreicht", "Regelstandard erreicht (MSA)", dat_bar$depVar)
dat_bar$depVar <- gsub("optErreicht", "Optimalstandard erreicht (MSA)", dat_bar$depVar)

## Order the data.frame:
dat_bar$y_axis_new <- paste0(dat_bar$state_var, dat_bar$depVar)
## Dummy-variable needed for sorting:
dat_bar$depVar_fac <- factor(dat_bar$depVar, levels = c(
  "Mindeststandard nicht erreicht (MSA)",
  "Regelstandard erreicht (MSA)",
  "Optimalstandard erreicht (MSA)"
))
dat_bar <- dat_bar[order(dat_bar$state_var, dat_bar$grouping_var, dat_bar$depVar_fac), ]

# Plot 1 ------------------------------------------------------------------

# lapply-loop for plotting each state, save result in list. Only for 2 states in this example:
plot_list <- lapply(unique(dat_bar$state_var)[1:2], function(x) {

  dat_bar_1 <- dat_bar[which(dat_bar$state_var == x), ]

  ## Build Land-column, where only the first Land is plotted
  dat_bar_1$y_axis <- paste0(dat_bar_1$grouping_var, dat_bar_1$depVar)
  dat_bar_1$grouping_var <- as.character(dat_bar_1$grouping_var)
  dat_bar_1$grouping_var[duplicated(dat_bar_1$grouping_var)] <- " "

  p_bar_1 <- plot_tablebar(
    dat = dat_bar_1,
    bar_est = "est_Trend_noComp_20112016_percent",
    bar_fill = "depVar",
    columns_table = c(
      "grouping_var",
      "depVar",
      "est_noTrend_noComp_2011_percent",
      "est_noTrend_noComp_2016_percent",
      "est_noTrend_noComp_2021_percent",
      "est_Trend_noComp_20112016_percent",
      "se_Trend_noComp_20112016_percent"
    ),
    headers = list(NULL, NULL, "%", "%", "%", "+/-", "(SE)", " "),
    columns_round = list(NULL, NULL, 1, 1, 1, 1, NULL),
    columns_table_se = list(NULL, NULL, NULL, NULL, NULL, NULL, "se_Trend_noComp_20112016_percent" ),
    column_spanners = list(
      "Leseverstehen" = c(1, 2),
      "2011" = 3,
      "2016" = 4,
      "2021" = 5,
      "Differenz 2016 - 2011" = c(6, 8)
    ),
    y_axis = "y_axis",
    plot_settings = plotsettings_tablebarplot(
      axis_x_lims = c(-20, 20),
      columns_alignment = c(0, 0, 2, 2, 2, 2, 0.5),
  columns_width = c(0.15, 0.3, 0.075, 0.075, 0.075, 0.075, 0.075, 0.175),
      default_list = barplot_plot_frz
    )
  )
  
  p_bar_2 <- plot_tablebar(
    dat = dat_bar_1,
    bar_est = "est_Trend_noComp_20162021_percent",
    bar_fill = "depVar",
    columns_table = c(
      "est_Trend_noComp_20162021_percent",
      "se_Trend_noComp_20162021_percent"
    ),
    headers = list("+/-", "(SE)", NULL),
    columns_round = list(1, NULL),
    columns_table_se = list(NULL, "se_Trend_noComp_20162021_percent"),
    column_spanners = list(
      "Differenz 2021 - 2016" = c(1, 3)
    ),
    y_axis = "y_axis",
    plot_settings = plotsettings_tablebarplot(
            axis_x_lims = c(-20, 22), # set higher than necessary so the last y-axis tick doesn't disappear into the left border
        columns_alignment = c(2, 0.5),
  columns_width = c(0.25, 0.25, 0.5),
      default_list = barplot_plot_frz
    )
  )

  p_bar_c <- combine_plots(list(p_bar_1, p_bar_2))
  
  return(p_bar_c)
})

## Name accordingly
names(plot_list) <- unique(dat_bar$state_var)[1:2]

## Plot one of the plots by Name:
plot_land_17 <- plot_list[["Land-17"]] 
plot_land_17

```

```{r, eval = FALSE}
## save all plots:
lapply(names(plot_list), function(p_name){
  p <- plot_list[[p_name]]
  save_plot(p, filename = paste0("../Kap_3_Frz_", p_name, ".pdf"), height = 226.2 / 4)
})

```


## Chapter 4
### Kompetenzwerte no Trend
```{r chapt_4_noTrend}
## As we want to plot both mean and sd - Parameters, we prepare the data 2x, once with mean and once with sd as chosen parameter:
dat_bar_mean <- prep_plot(trend_books,
  competence = "lesen",
  grouping_vars = "KBuecher_imp3",
  parameter = "mean"
)[["plot_tablebar"]]

dat_bar_sd <- prep_plot(trend_books,
  competence = "lesen",
  grouping_vars = "KBuecher_imp3",
  parameter = "sd"
)[["plot_tablebar"]]

## ... then we merge:
dat_bar_mean_sd <- merge(dat_bar_mean,
  dat_bar_sd,
  by = c("state_var", "grouping_var"),
  suffix = c("_mean", "_sd")
)

## Filter all rows containg the whole state (not subgroups):
dat_bar_mean_sd <- dat_bar_mean_sd[dat_bar_mean_sd$grouping_var == "noGroup", ]

## ... and plot:
mean_noTrend <- plot_tablebar(dat_bar_mean_sd,
  bar_est = "est_noTrend_Comp_crossDiff_wholeGroup_2021_mean",
  bar_sig = "sig_noTrend_Comp_crossDiff_wholeGroup_2021_mean",
  columns_table = list(
    "state_var",
    "est_noTrend_noComp_2021_mean",
    "se_noTrend_noComp_2021_mean",
    "est_noTrend_noComp_2021_sd",
    "se_noTrend_noComp_2021_sd"
  ),
  headers = list("**Land**", # ** for bold
                 "***M***", # *** for bold and italic,
                 "***(SE)***", 
                 "***SD***", 
                 "***(SE)***",  
                 "**Abweichung vom Mittelwert <br> für Deutschland**"), # <br> for linebreak, 
  columns_table_sig_bold = list(NULL, "sig_noTrend_Comp_crossDiff_wholeGroup_2021_mean", NULL, "sig_noTrend_Comp_crossDiff_wholeGroup_2021_sd", NULL), 
  columns_table_se = list(NULL, NULL, "se_noTrend_noComp_2021_mean", NULL, "se_noTrend_noComp_2021_sd"),
  y_axis = "state_var",
  plot_settings = plotsettings_tablebarplot(
    background_stripes_colour = c(rep(c("white", "gray94"), 8), "gray87"),
    bar_background_lines = "scale_breaks", # set background lines at scalebreaks
    bar_background_lines_linetype = "solid",
    bar_pattern_width = 0.5, # Increase the size of the white stripes. 
    columns_alignment = c(0, 0.5, 0.5, 0.5, 0.5),
    columns_width = c(0.2, 0.1, 0.1, 0.1, 0.1, 0.4),
    headers_alignment = c(0, 0.5, 0.5, 0.5, 0.5, 0.5),
    headers_background_width_y = 1, # Increase the header background width, so the linebreak doesn't run over plot borders
    default_list = barplot_table_plot_pattern
  )
)

mean_noTrend
```

```{r, eval = FALSE}
save_plot(mean_noTrend, filename = "../Kap4_2021_noTrend.pdf", height = 226.2 / 3)
```





