---
title: "Lineplots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lineplots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette shows you how to plot lineplots from `eatRep` data. The workflow is optimized for Bildungstrend-graphs, but can be expanded for plotting other `eatRep` data as well. 

## Data preparation
```{r load_package}
library(eatPlot)

```

The first step in the workflow always is the data preparation. This is needed to bring the data into the correct format for plotting. When getting data from `eatRep`, it will look something like this:

```{r}
str(trend_3)
```

It can make sense to pre-process the data a bit, 


```{r lineplot_states} 
trend_3_subset <- trend_3
trend_3_subset$group <- subset(trend_3_subset$group, trend_3_subset$group$mhg %in% c("einET", "ersteGen", "total"))

## hier nur die nehmen, die "- total" in TR_BUNDESLAND enthalten 

trend_3_prepped <- prep_lineplot(
  trend_3_subset,
  parameter = "mean",
  used_comparisons = c("none", "trend", "crossDiffTotal", "crossDiff") ## evtl. auch einfach davor filtern?
)

```


```{r}

p <- plot_lineplot(trend_3_prepped,
  point_est = "est_comparison_none",
  point_sig = "sig_comparison_crossDiffTotal", ## sig_noTrend_Comp_crossDiff_wholeGroup
  line_est = "est_comparison_none",
  line_sig = "sig_comparison_trend",
  line_se = "se_comparison_none",
  brace_label_est = "est_comparison_trend",
  brace_label_sig = "sig_comparison_trend",
  brace_label_se = "se_comparison_trend",
  brace_label_sig_high = NULL,
  brace_label_sig_bold = "sig_comparison_trend",
  years_lines = list(c(2009, 2015), c(2015, 2022)),
  years_braces = list(c(2009, 2015), c(2015, 2022)),
  subgroup_var = "mhg",
  background_facet = "total",
  background_subgroup = "total",
  facet_var = "TR_BUNDESLAND",
  seperate_plot_var_box = "wholeGroup",
  title_superscripts = NULL,
  plot_settings = plotsettings_lineplot(split_plot = FALSE, default_list = lineplot_4x4)
)

# save_plot(p, filename = "/home/nick/Downloads/test.pdf")
# save_plot(p, filename = "C:/Users/hafiznij/Downloads/test.pdf")
```

