---
title: "Lineplots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lineplots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette shows you how to plot lineplots from `eatRep` data. The workflow is optimized for Bildungstrend-graphs, but can be expanded for plotting other `eatRep` data as well. 

```{r load_package}
library(eatPlot)
```


## Lineplot for one group

Let's take example data from the `trend_mw` example dataset.
The first step in the workflow always is the data preparation.
This is needed to bring the `eatRep` data into the correct format for plotting. 

```{r}
dat_lineplot_1 <- prep_lineplot(
  trend_gender[[1]],
  subgroup_var = "Kgender" ## Leave this argument if you have only one subgroup
)
```

It might be necessary to do some slight manual data preparation:

```{r}
## Don't do that if you only have one group in your data, or want to plot all groups
dat_lineplot_1 <- subset(dat_lineplot_1, subgroup_var == "total")

## For correctly displaying the state names:
dat_lineplot_1$state_var <- process_bundesland(dat_lineplot_1$state_var)
```

And then we can already plot:

```{r}
lineplot_1 <- plot_lineplot(dat_lineplot_1,
  years_lines = list(c(2009, 2015), c(2015, 2022)),
  years_braces = list(c(2009, 2015), c(2015, 2022)),
  plot_settings = plotsettings_lineplot(
default_list = lineplot_4x4)
) #+
  #ggview:: canvas(160, 180, units = "mm")
```

```{r save lineplot_1_group}
#| eval: false
save_plot(lineplot_1, filename = "C:/Users/hafiznij/Downloads/lineplot_1_group.pdf", width = 160, height = 185, ,scaling = 1)
```

```{r}
#| echo: false
lineplot_1
```


## Lineplot for two groups

```{r lineplot_states} 
dat_lineplot_2 <- prep_lineplot(
  trend_gender[[1]],
  subgroup_var = "Kgender"
)

dat_lineplot_2$state_var <- process_bundesland(dat_lineplot_2$state_var)


## We can set the order of the brace labels by setting the factor levels of the subgroup_var:
dat_lineplot_2$subgroup_var <- factor(dat_lineplot_2$subgroup_var, levels = c("weiblich", "maennlich", "total"), ordered = TRUE)

lineplot_2 <- plot_lineplot(
  dat_lineplot_2,
  years_lines = list(c(2009, 2015), c(2015, 2022)),
  years_braces = list(c(2009, 2015), c(2015, 2022)),
  background_subgroup = "total",
  plot_settings = plotsettings_lineplot(
    subgroup_colours = c(weiblich = "black", maennlich = cmyk(0, 0, 0, 60)), ## Here we determine the colours of the subgroups
    default_list = lineplot_4x4
  )
) 
```

```{r}
#| eval: false
save_plot(lineplot_2, filename = "C:/Users/hafiznij/Downloads/lineplot_2_groups.pdf", width = 160, height = 185, scaling = 1)
```

```{r}
lineplot_2
```




## Lineplot for whole Germany 3x2


```{r}

trend_ger <- do.call(rbind, lapply(trend_gender, prep_lineplot, subgroup_var = "Kgender"))
trend_ger <- subset(trend_ger, state_var == "total")
trend_ger$subgroup_var <- factor(trend_ger$subgroup_var, levels = c("weiblich", "maennlich", "total"), ordered = TRUE)
trend_ger$kb <- gsub("hoeren", "Hören", trend_ger$kb)
trend_ger$kb <- gsub("lesen", "Lesen", trend_ger$kb)

trend_ger_2 <- trend_ger
trend_ger_3 <- trend_ger

trend_ger_2$kb <- gsub("Lesen", "Englisch: Reading", trend_ger_2$kb)
trend_ger_2$kb <- gsub("Hören", "Englisch: Listening", trend_ger_2$kb)


trend_ger_3$kb <- gsub("Lesen", "Biologie: Fachwissen", trend_ger_3$kb)
trend_ger_3$kb <- gsub("Hören", "Biologie: Erkenntnisgewinnung", trend_ger_3$kb)


trend_total <- rbind(trend_ger, trend_ger_2, trend_ger_3)
```

```{r}
lineplot_germany <- plot_lineplot(
  trend_total,
 point_sig = NULL,
  years_lines = list(c(2009, 2015), c(2015, 2022)),
  years_braces = list(c(2009, 2015), c(2015, 2022)),
  facet_var = "kb",
  # background_facet = "total",
  background_subgroup = "total",
  plot_settings = plotsettings_lineplot(
    brace_label_nudge_x = 0.21,
    split_plot = FALSE,
    background_lines = TRUE,
    subgroup_colours = c(weiblich = "#000000", maennlich = cmyk(0, 0, 0, 60)), ## Here we determine the colours of the subgroups
   # margin_top = 0,
  # margin_bottom = 0,
    n_cols = 2, 
    default_list = lineplot_4x4
  )
) 
```

```{r}
#| eval: false
save_plot(lineplot_germany, filename = "C:/Users/hafiznij/Downloads/lineplot_2_groups_germany_3x2.pdf", height = 185, width = 118, scaling = 1)
```


## Lineplot for whole Germany 2x3 with split plot
```{r}
lineplot_germany <- plot_lineplot(
  trend_total,
 point_sig = NULL,
  years_lines = list(c(2009, 2015), c(2015, 2022)),
  years_braces = list(c(2009, 2015), c(2015, 2022)),
  facet_var = "kb",
  # background_facet = "total",
  background_subgroup = "total",
  plot_settings = plotsettings_lineplot(
    brace_label_nudge_x = 0.21,
    split_plot = FALSE,
    background_lines = TRUE,
    subgroup_colours = c(weiblich = "#000000", maennlich = cmyk(0, 0, 0, 60)), ## Here we determine the colours of the subgroups
   # margin_top = 0,
  # margin_bottom = 0,
    n_cols = 3, 
  equal_trend_line_length = TRUE,
    default_list = lineplot_4x4
  )
) 
```

```{r}
#| eval: false
save_plot(lineplot_germany, filename = "C:/Users/hafiznij/Downloads/lineplot_2_groups_germany2x3.pdf", height = 185*2/3, width = 160, scaling = 1)
```

