---
title: "Lineplots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lineplots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette shows you how to plot lineplots from `eatRep` data. The workflow is optimized for Bildungstrend-graphs, but can be expanded for plotting other `eatRep` data as well. 

## Data preparation
```{r load_package}
library(eatPlot)
```

The first step in the workflow always is the data preparation. This is needed to bring the data into the correct format for plotting. When getting data from `eatRep`, it will look something like this:

```{r}
#| eval: false
str(trend_3)
```

It can make sense to pre-process the data a bit, 


```{r lineplot_states} 
trend_3_subset <- trend_mw

trend_3_prepped <- prep_lineplot(
  trend_3_subset,
  subgroup_var = "geschlecht"
)


trend_3_prepped$TR_BUNDESLAND <- gsub("ue", "ü", trend_3_prepped$TR_BUNDESLAND)
```


```{r}
lineplot_2 <- plot_lineplot(
  trend_3_prepped,
  years_lines = list(c(2009, 2015), c(2015, 2022)),
  years_braces = list(c(2009, 2015), c(2015, 2022)),
  background_subgroup = "total",
  plot_settings = plotsettings_lineplot(split_plot = FALSE, default_list = lineplot_4x4)
)

## Jetzt wird Background line irgendwo nicht rausgefiltert. 
```

```{r save lineplot_2}
#| eval: false
save_plot(lineplot_2, filename = "C:/Users/hafiznij/Downloads/lineplot_2_groups.pdf")
```


## Lineplot for whole Germany


```{r lineplot_germany} 
trend_ger <- prep_lineplot(
  trend_mw,
  subgroup_var = "geschlecht"
)

trend_ger_lesen <- trend_ger
trend_ger_lesen$kb <- "Lesen"

trend_total <- rbind(trend_ger, trend_ger_lesen)
trend_total$kb <- gsub("hoeren", "Hören", trend_total$kb)

trend_total <- subset(trend_total, TR_BUNDESLAND == "total") |>
  subset(geschlecht %in% c("m", "w"))

trend_total$TR_BUNDESLAND <- gsub("ue", "ü", trend_total$TR_BUNDESLAND)
```

```{r}
lineplot_germany_2 <- plot_lineplot(trend_total,
  years_lines = list(c(2009, 2015), c(2015, 2022)),
  years_braces = list(c(2009, 2015), c(2015, 2022)),
  facet_var = "kb",
  title_superscripts = NULL,
  plot_settings = plotsettings_lineplot(
    brace_label_nudge_x = 0.3,
    split_plot = FALSE,
    background_lines = FALSE,
    default_list = lineplot_4x4
  )
)
```

```{r save lineplot_germany_2_groups}
#| eval: false
save_plot(lineplot_germany_2, filename = "C:/Users/hafiznij/Downloads/lineplot_deutschland.pdf", height = 226.2 / 4)
```


## Lineplot one group

```{r}
trend_3_prepped <- prep_lineplot(
  trend_mw,
  subgroup_var = "geschlecht"
)

trend_3_prepped <- subset(trend_3_prepped, subgroup_var == "total")

trend_3_prepped$TR_BUNDESLAND <- gsub("ue", "ü", trend_3_prepped$TR_BUNDESLAND)


lineplot_1 <- plot_lineplot(trend_3_prepped,
  years_lines = list(c(2009, 2015), c(2015, 2022)),
  years_braces = list(c(2009, 2015), c(2015, 2022)),
  plot_settings = plotsettings_lineplot(split_plot = FALSE, default_list = lineplot_4x4)
)
```

```{r save lineplot_1_group}
#| eval: false
save_plot(lineplot_1, filename = "C:/Users/hafiznij/Downloads/lineplot_1_group.pdf")
```


## Workshop example
```{r}
#| eval: FALSE
trend_dat <- readRDS("I:/Methoden/02_IQB-interne_eat_Workshops/eatRep_2024/Beispieloutputs/04_meansAufbereitet.rds")


trend_p <- prep_lineplot(
  trend_dat
)

str(trend_p)
``` 


```{r}
#| eval: FALSE


trend_p$TR_BUNDESLAND <- gsub("([a-z])([A-Z])", "\\1-\\2", trend_p$TR_BUNDESLAND)
trend_p$TR_BUNDESLAND <- gsub("ue", "ü", trend_p$TR_BUNDESLAND)


lineplot_1_w <- plot_lineplot(
  trend_p,
  years_lines = list(c(2009, 2015), c(2015, 2022)),
  years_braces = list(c(2009, 2015), c(2015, 2022)),
  box_facet = "Berlin",
  background_subgroup = "total",
  title_superscripts = list(
    "Bayern" = "a",
    "Thüringen" = "3"),
  plot_settings = plotsettings_lineplot(default_list = lineplot_4x4)
)
```

```{r save lineplot_1_group_w}
#| eval: false
save_plot(lineplot_1_w, filename = "C:/Users/hafiznij/Downloads/lineplot_1_group_workshop.pdf")
```
