---
title: "Lineplots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lineplots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette shows you how to plot lineplots from `eatRep` data. The workflow is optimized for Bildungstrend-graphs, but can be expanded for plotting other `eatRep` data as well. 

## Data preparation
```{r load_package}
library(eatPlot)

```

The first step in the workflow always is the data preparation. This is needed to bring the data into the correct format for plotting. When getting data from `eatRep`, it will look something like this:

```{r}
str(trend_3)
```

It can make sense to pre-process the data a bit, 


```{r lineplot_states} 
trend_3_subset <- trend_mw

trend_3_prepped <- prep_lineplot(
  trend_3_subset,
  parameter = "mean")


```


```{r}

p <- plot_lineplot(trend_3_prepped,
  point_est = "est_comparison_none",
  point_sig = "sig_comparison_crossDiffTotal", ## sig_noTrend_Comp_crossDiff_wholeGroup
  line_est = "est_comparison_none",
  line_sig = "sig_comparison_trend",
  line_se = "se_comparison_none",
  brace_label_est = "est_comparison_trend",
  brace_label_sig = "sig_comparison_trend",
  brace_label_se = "se_comparison_trend",
  brace_label_sig_high = NULL,
  brace_label_sig_bold = "sig_comparison_trend",
  years_lines = list(c(2009, 2015), c(2015, 2022)),
  years_braces = list(c(2009, 2015), c(2015, 2022)),
  subgroup_var = "geschlecht",
  background_facet = "total",
  background_subgroup = "total",
  facet_var = "TR_BUNDESLAND",
  seperate_plot_var_box = "wholeGroup",
  title_superscripts = NULL,
  plot_settings = plotsettings_lineplot(split_plot = FALSE, default_list = lineplot_4x4)
)

# save_plot(p, filename = "/home/nick/Downloads/test.pdf")
# save_plot(p, filename = "C:/Users/hafiznij/Downloads/lineplot_2_groups.pdf")
```


## Lineplot for whole Germany


```{r lineplot_germany} 
trend_ger <- prep_lineplot(
  trend_mw,
  parameter = "mean")

trend_ger_lesen <- trend_ger 
trend_ger_lesen$kb <- "lesen"

trend_total <- rbind(trend_ger, trend_ger_lesen)

trend_total <- subset(trend_total, TR_BUNDESLAND == "total") |>
  subset(geschlecht %in% c("m", "w"))


```

```{r}
p <- plot_lineplot(trend_total,
  point_est = "est_comparison_none",
  point_sig = NULL,
  line_est = "est_comparison_none",
  line_sig = "sig_comparison_trend",
  line_se = "se_comparison_none",
  brace_label_est = "est_comparison_trend",
  brace_label_sig = "sig_comparison_trend",
  brace_label_se = "se_comparison_trend",
  brace_label_sig_high = NULL,
  brace_label_sig_bold = "sig_comparison_trend",
  years_lines = list(c(2009, 2015), c(2015, 2022)),
  years_braces = list(c(2009, 2015), c(2015, 2022)),
  subgroup_var = "geschlecht",
  background_facet = NULL,
  background_subgroup = NULL,
  facet_var = "kb",
  seperate_plot_var_box = "wholeGroup",
  title_superscripts = NULL,
  plot_settings = plotsettings_lineplot(split_plot = FALSE, background_lines = FALSE, default_list = lineplot_4x4)
)
```

```{r}
save_plot(p, filename = "C:/Users/hafiznij/Downloads/lineplot_deutschland.pdf", height = 226.2/4 + 10)

```


## Lineplot one group

```{r}
trend_3_prepped <- prep_lineplot(
  trend_mw,
  parameter = "mean")

trend_3_prepped <- subset(trend_3_prepped, geschlecht == "total")

p <- plot_lineplot(trend_3_prepped,
  point_est = "est_comparison_none",
  point_sig = "sig_comparison_crossDiffTotal", ## sig_noTrend_Comp_crossDiff_wholeGroup
  line_est = "est_comparison_none",
  line_sig = "sig_comparison_trend",
  line_se = "se_comparison_none",
  brace_label_est = "est_comparison_trend",
  brace_label_sig = "sig_comparison_trend",
  brace_label_se = "se_comparison_trend",
  brace_label_sig_high = NULL,
  brace_label_sig_bold = "sig_comparison_trend",
  years_lines = list(c(2009, 2015), c(2015, 2022)),
  years_braces = list(c(2009, 2015), c(2015, 2022)),
  subgroup_var = "geschlecht",
  background_facet = "total",
  background_subgroup = "total",
  facet_var = "TR_BUNDESLAND",
  seperate_plot_var_box = "wholeGroup",
  title_superscripts = NULL,
  plot_settings = plotsettings_lineplot(split_plot = FALSE, default_list = lineplot_4x4)
)

# save_plot(p, filename = "/home/nick/Downloads/test.pdf")
# save_plot(p, filename = "C:/Users/hafiznij/Downloads/lineplot_2_groups.pdf")
```

```

