---
title: "Lineplots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lineplots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette shows you how to plot lineplots from `eatRep` data. The workflow is optimized for Bildungstrend-graphs, but can be expanded for plotting other `eatRep` data as well. 

```{r load_package}
library(eatPlot)
```


## Lineplot for one group

Let's take example data from the `trend_mw` example dataset.
The first step in the workflow always is the data preparation.
This is needed to bring the `eatRep` data into the correct format for plotting. 

```{r}
dat_lineplot_1 <- prep_lineplot(
  trend_mw,
  subgroup_var = "geschlecht" ## Leave this argument if you have only one subgroup
)
```

It might be necessary to do some slight manual data preparation:

```{r}
## Don't do that if you only have one group in your data, or want to plot all groups
dat_lineplot_1 <- subset(dat_lineplot_1, subgroup_var == "total")

## For correctly displaying the state names:
dat_lineplot_1 <- process_bundesland(dat_lineplot_1)
```

And then we can already plot:

```{r}
lineplot_1 <- plot_lineplot(dat_lineplot_1,
  years_lines = list(c(2009, 2015), c(2015, 2022)),
  years_braces = list(c(2009, 2015), c(2015, 2022)),
  plot_settings = plotsettings_lineplot(default_list = lineplot_4x4)
)
```

```{r save lineplot_1_group}
#| eval: false
save_plot(lineplot_1, filename = "C:/Users/hafiznij/Downloads/lineplot_1_group.pdf")
```

```{r}
#| echo: false
lineplot_1
```


## Lineplot for two groups

```{r lineplot_states} 
dat_lineplot_2 <- prep_lineplot(
  trend_mw,
  subgroup_var = "geschlecht"
)
dat_lineplot_2 <- process_bundesland(dat_lineplot_2)

lineplot_2 <- plot_lineplot(
  dat_lineplot_2,
  years_lines = list(c(2009, 2015), c(2015, 2022)),
  years_braces = list(c(2009, 2015), c(2015, 2022)),
  background_subgroup = "total",
  plot_settings = plotsettings_lineplot(default_list = lineplot_4x4)
)
```

```{r}
#| eval: false
save_plot(lineplot_2, filename = "C:/Users/hafiznij/Downloads/lineplot_2_groups.pdf")
```

```{r}
lineplot_2
```

<!-- ## Lineplot for whole Germany -->


<!-- ```{r lineplot_germany}  -->

<!-- trend_ger <- prep_lineplot( -->
<!--   trend_mw, -->
<!--   subgroup_var = "geschlecht" -->
<!-- ) -->

<!-- ## This is data preperation for the example and will be updated as soon as I have example data with multiple Kompetenzbereichen: -->

<!-- trend_ger_lesen <- trend_ger -->
<!-- trend_ger_lesen$kb <- "Lesen" -->

<!-- trend_total <- rbind(trend_ger, trend_ger_lesen) -->
<!-- trend_total$kb <- gsub("hoeren", "Hören", trend_total$kb) -->

<!-- trend_total <- subset(trend_total, TR_BUNDESLAND == "total") -->

<!-- trend_total$TR_BUNDESLAND <- gsub("ue", "ü", trend_total$TR_BUNDESLAND) -->
<!-- ``` -->

<!-- ```{r} -->

<!-- ## Hier fehlt noch der Hintergrund für ganz Deutschland -->
<!-- lineplot_germany_2 <- plot_lineplot(trend_total, -->
<!--   years_lines = list(c(2009, 2015), c(2015, 2022)), -->
<!--   years_braces = list(c(2009, 2015), c(2015, 2022)), -->
<!--   facet_var = "kb", -->
<!--   background_facet = NULL, -->
<!--   background_subgroup = "total", -->
<!--   plot_settings = plotsettings_lineplot( -->
<!--     brace_label_nudge_x = 0.3, -->
<!--     split_plot = FALSE, -->
<!--     background_lines = FALSE, -->
<!--     default_list = lineplot_4x4 -->
<!--   ) -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r save lineplot_germany_2_groups} -->
<!-- #| eval: false -->
<!-- save_plot(lineplot_germany_2, filename = "C:/Users/hafiznij/Downloads/lineplot_deutschland.pdf", height = 226.2 / 4) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- lineplot_germany_2 -->
<!-- ``` -->

