---
title: "Mehrere Kompetenzbereiche: Schleifen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{loop_example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(eatPlot)
```

## Data preperation

The data we are using in this example is nexted into multiple competence areas. 
Let's take a look: 

```{r}
str(dispar)
```

We have multiple competence areas:

```{r}
names(dispar)
```

To build plots for all competence areas, I'd suggest to follow these three steps:

1. Build one plot.
2. Adjust it, until you are satisfied.
3. Put it into a function. 
3. Use `lapply()` to loop over the competence areas and build the plots from the function defined in step 2.

## 1. Build the plot
Our goal is to build [Abbildung 6.6](https://nickhaf.github.io/eatPlot/articles/tableplots.html#abbildung-6-6).   Let's take `hoeren` for our prototype:

```{r}
str(dispar$hoeren)
```

First, I need to search for an appropriate template on this website. 
Luckily, we already have a template for  [Abbildung 6.6](https://nickhaf.github.io/eatPlot/articles/tableplots.html#abbildung-6-6). 
So ewe only need to follow it!  
To do this, I first have to look up how my subgroup variable is called. 
I can find this out easiest by looking at the `group` or the `plain` data.frame:

```{r}
str(dispar$hoeren$group)

```

My subgroup variable is called `Kgender`.
Now I can use the `prep_tablebarplot()` function to prepare the data for plotting. 
Of course I have to put my own data into this function:

```{r}
dat_6.6 <- prep_tablebarplot(
  dispar$hoeren, ## My data.frame
  subgroup_var = "Kgender", ## The subgroup variable
  par = c("mean", "sd") ## We need both mean and sd for the plot
)
```

This is our prepared data.

### Data wrangling

For this specific plot, we also have to do some additional (but simple) data transformation, because the data will be plotted in the same order, as we give it into the function. 
First of all, we can subset the subgroup variable to only extract the groups, we want to use in the plot:

```{r}
gender_hoeren <- subset(dat_6.6, subgroup_var %in% c("maennlich", "weiblich"))
```

In this BT, the girls should always be on top. 
To achieve this, we have to sort our data:

```{r}
gender_hoeren <- gender_hoeren[order(gender_hoeren$subgroup_var, decreasing = TRUE), ]
gender_hoeren <- gender_hoeren[order(gender_hoeren$state_var), ]

```

Also, we only want to write the Bundesland into the plot every second row, so let's remove duplicates:

```{r}
gender_hoeren$state_var[duplicated(gender_hoeren$state_var)] <- " "
```

We can use the `process_bundesland()` function to add dashes and replace umlauts.
We also want to break the Bundesländer names, if they are too long, so we set `linebreak = TRUE`:

```{r}
gender_hoeren$state_var <- process_bundesland(gender_hoeren$state_var, linebreak = TRUE)
```

Finally, we have to rename the groups to "Jungen" and "Mädchen" and add an empty column, which will be used as a separator later on:

```{r}
gender_hoeren$subgroup_var <- gsub("maennlich", "Jungen", gender_hoeren$subgroup_var)
gender_hoeren$subgroup_var <- gsub("weiblich", "Mädchen", gender_hoeren$subgroup_var)

gender_hoeren$empty <- ""
```

That's it. 
The data now has the correct format for plotting.  

### Plotting

Because we want to plot two plots next to each other, we need to set the column widths of both plots to be the same:

```{r}
column_widths_stand <- standardize_column_width(
  column_widths = list(
    p1 = c(0.085, 0.05, rep(0.035, 6), 0.015, rep(0.035, 3), NA),
    p2 = c(rep(0.035, 3), NA)
  ),
  plot_ranges = c(142, 142) # Ranges of the x-axes of both plots set in 'axis_x_lims'.
)
```

To build the tables, we only copy paste from the template on the website:

```{r}

p_1 <- plot_tablebarplot(
  dat = gender_hoeren,
  bar_est = "est_mean_comp_trend_sameFacet_sameSubgroup_2009_2015",
  bar_label = NULL,
  bar_sig = "sig_mean_comp_trend_sameFacet_sameSubgroup_2009_2015",
  bar_fill = "subgroup_var",
  column_spanners = list(
    "**2009**" = c(3, 4),
    "**2015**" = c(5, 6),
    "**2022**" = c(7, 8),
    "**Differenz 2015-2009**" = c(10, 13)
  ),
  columns_table_se = list(NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, "se_mean_comp_trend_sameFacet_sameSubgroup_2009_2015", NULL),
  headers = list("**Land**", " ", "*M*", "*SD*", "*M*", "*SD*", "*M*", "*SD*", "", "*M<sub>2015</sub>-<br>M<sub>2009</sub>* ", "*(SE)*", "*d*", " "),
  columns_table = c("state_var", "subgroup_var", "est_mean_comp_none_2009", "est_sd_comp_none_2009", "est_mean_comp_none_2015", "est_sd_comp_none_2015", "est_mean_comp_none_2022", "est_sd_comp_none_2022", "empty", "est_mean_comp_trend_sameFacet_sameSubgroup_2009_2015", "se_mean_comp_trend_sameFacet_sameSubgroup_2009_2015", "es_mean_comp_trend_sameFacet_sameSubgroup_2009_2015"),
  columns_table_sig_bold = list(
    NULL, NULL, "sig_mean_comp_none_2009",
    NULL, "sig_mean_comp_none_2015", NULL, "sig_mean_comp_none_2022", NULL, NULL, "sig_mean_comp_trend_sameFacet_sameSubgroup_2009_2015", NULL, "sig_mean_comp_trend_sameFacet_sameSubgroup_2009_2015"
  ),
  columns_table_sig_superscript = list(NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, "sig_mean_comp_trend_crossDiff_totalFacet_sameSubgroup_2009_2015", NULL, NULL),
  y_axis = "y_axis",
  columns_round = c(rep(0, 11), 2),
  plot_settings = plotsettings_tablebarplot(
    bar_pattern_spacing = 0.0159, ## We calculated this below in standardize_pattern_spacing()
    columns_alignment = c(0, 0, rep(2, 10)),
    columns_width = column_widths_stand$p1, ## This is the column-width object we set above
    columns_nudge_y = c(-0.5, rep(0, 11)),
    headers_alignment = c(0, 0, rep(0.5, 7), 0, 0.5, 0.5, 0),
    headers_row_height = 1.75,
    headers_nudge_x = c(rep(0, 9), 2, rep(0, 3)),
    default_list = abb_6.6
  )
)


p_2 <- plot_tablebarplot(
  dat = gender_hoeren,
  bar_est = "est_mean_comp_trend_sameFacet_sameSubgroup_2015_2022",
  bar_label = NULL,
  bar_sig = "sig_mean_comp_trend_sameFacet_sameSubgroup_2009_2015",
  bar_fill = "subgroup_var",
  column_spanners = list(
    "**Differenz 2022-2015**" = c(1, 4)
  ),
  headers = list(
    "*M<sub>2022</sub>-<br>M<sub>2015</sub>* ",
    "*(SE)*",
    "*d*",
    " "
  ),
  columns_table = c(
    "est_mean_comp_trend_sameFacet_sameSubgroup_2015_2022",
    "se_mean_comp_trend_sameFacet_sameSubgroup_2015_2022",
    "es_mean_comp_trend_sameFacet_sameSubgroup_2015_2022"
  ),
  columns_table_se = list(NULL, "se_mean_comp_trend_sameFacet_sameSubgroup_2015_2022", NULL),
  columns_table_sig_bold = list("sig_mean_comp_trend_sameFacet_sameSubgroup_2015_2022", NULL, "sig_mean_comp_trend_sameFacet_sameSubgroup_2015_2022"),
  columns_table_sig_superscript = list("sig_mean_comp_trend_crossDiff_totalFacet_sameSubgroup_2015_2022", NULL, NULL),
  y_axis = "y_axis",
  columns_round = c(0, 0, 2),
  plot_settings = plotsettings_tablebarplot(
    bar_pattern_spacing = 0.0341, ## We calculated this below in standardize_pattern_spacing()
    columns_alignment = c(2, 2, 2),
    columns_width = column_widths_stand$p2, ## This is the column-width object we set above
    headers_nudge_x = c(2, 0, 0, 0),
    headers_alignment = c(0, 0.5, 0.5, 0),
    headers_row_height = 1.75,
    default_list = abb_6.6
  )
)


```

For the patterns in the bars to have the same widht, we need to set the spacing between them:
```{r}
bar_pattern_spacing_stand <- standardize_pattern_spacing(list(p_1, p_2), pattern_spacing = 0.05)
bar_pattern_spacing_stand
```

(Rebuild the plot with these pattern spacings)

Finally, we can combine the plots:

```{r}
tableplot_6.6 <- combine_plots(list(p_1, p_2))
```

## 2. Adjustments

Now we can fine/tune the plot, like setting the column widths, nudge the headers into the right position, etc. 
You have to look at the plot in the right format so the changes are shown in the correct proportions. 
Either save them as PDF, or use the `ggview` package:

```{r}
#| eval: false

p <- tableplot_6.6 +
  ggview::canvas(
    235, 130,
    units = "mm"
  )
p
```

(You have to re-evaluate the plot without the `canvas()` function before saving it though.)

If everything is satisfactory, we can save the plot. 


```{r}
#| eval: false
save_plot(tableplot_6.6, filename = "C:/Users/hafiznij/Downloads/abb_6.6.pdf", width = 235, height = 130, scaling = 1)
```


## 3. Put it into a function
As soon as the plot basis works, we can put the code into a dedicated function, to pack it away:

```{r}
## Data Prep
prepare_6.6_data <- function(dat_kb) {
  dat_6.6 <- prep_tablebarplot(
    dat_kb,
    subgroup_var = "Kgender",
    par = c("mean", "sd") ## We need both mean and sd for the plot
  )


  ## Jetzt müssen wir die Daten noch ein wenig für unseren spezifischen Plot umformen
  ## Wir wollen nur männlich und weiblich plotten:
  dat_6.6 <- subset(dat_6.6, subgroup_var %in% c("maennlich", "weiblich"))

  ## Mädchen sollen nach oben, d.h. wir sortieren zuerst absteigend alphabetisch, und dann nach den Bundesländern, um diese wieder in die richtige Reihenfolge zu bekommen
  dat_6.6 <- dat_6.6[order(dat_6.6$subgroup_var, decreasing = TRUE), ]
  dat_6.6 <- dat_6.6[order(dat_6.6$state_var), ]

  ## Dann soll nur in jeder zweiten Zeile das Bundesland geplotted werden, wir entfernen also Duplikate:
  dat_6.6$state_var[duplicated(dat_6.6$state_var)] <- " "

  ## Mit process_bundesland() können wir Bindestriche einfügen und Umlaute austauschen.
  ## linebreak = TRUE damit Bundesländer die aus zwei Wörten bestehen umgebrochen werden
  dat_6.6$state_var <- process_bundesland(dat_6.6$state_var, linebreak = TRUE)

  ## Dann müssen wir noch die Gruppen in Jungen und Mädchen umbenennen
  dat_6.6$subgroup_var <- gsub("maennlich", "Jungen", dat_6.6$subgroup_var)
  dat_6.6$subgroup_var <- gsub("weiblich", "Mädchen", dat_6.6$subgroup_var)

  ## Und eine leere Spalte erzeugen, die später als Trenner dient
  dat_6.6$empty <- ""

  return(dat_6.6)
}

## Plotting
plot_6.6 <- function(dat_prepped) {
  column_widths_stand <- standardize_column_width(
    column_widths = list(
      p1 = c(0.085, 0.05, rep(0.035, 6), 0.015, rep(0.035, 3), NA),
      p2 = c(rep(0.035, 3), NA)
    ),
    plot_ranges = c(140, 142) # Ranges of the x-axes of both plots set in 'axis_x_lims'.
  )


  ## 3. Tabellen erzeugen:
  ## Dafür copy-pasten wir einfach von der Vorlage:

  p_1 <- plot_tablebarplot(
    dat = dat_prepped,
    bar_est = "est_mean_comp_trend_sameFacet_sameSubgroup_2009_2015",
    bar_label = NULL,
    bar_sig = "sig_mean_comp_trend_sameFacet_sameSubgroup_2009_2015",
    bar_fill = "subgroup_var",
    column_spanners = list(
      "**2009**" = c(3, 4),
      "**2015**" = c(5, 6),
      "**2022**" = c(7, 8),
      "**Differenz 2015-2009**" = c(10, 13)
    ),
    columns_table_se = list(NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, "se_mean_comp_trend_sameFacet_sameSubgroup_2009_2015", NULL),
    headers = list("**Land**", " ", "*M*", "*SD*", "*M*", "*SD*", "*M*", "*SD*", "", "*M<sub>2015</sub>-<br>M<sub>2009</sub>* ", "*(SE)*", "*d*", " "),
    columns_table = c("state_var", "subgroup_var", "est_mean_comp_none_2009", "est_sd_comp_none_2009", "est_mean_comp_none_2015", "est_sd_comp_none_2015", "est_mean_comp_none_2022", "est_sd_comp_none_2022", "empty", "est_mean_comp_trend_sameFacet_sameSubgroup_2009_2015", "se_mean_comp_trend_sameFacet_sameSubgroup_2009_2015", "es_mean_comp_trend_sameFacet_sameSubgroup_2009_2015"),
    columns_table_sig_bold = list(
      NULL, NULL, "sig_mean_comp_none_2009",
      NULL, "sig_mean_comp_none_2015", NULL, "sig_mean_comp_none_2022", NULL, NULL, "sig_mean_comp_trend_sameFacet_sameSubgroup_2009_2015", NULL, "sig_mean_comp_trend_sameFacet_sameSubgroup_2009_2015"
    ),
    columns_table_sig_superscript = list(NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, "sig_mean_comp_trend_crossDiff_totalFacet_sameSubgroup_2009_2015", NULL, NULL),
    y_axis = "y_axis",
    columns_round = c(rep(0, 11), 2),
    plot_settings = plotsettings_tablebarplot(
      axis_x_lims = c(-70, 70),
      bar_pattern_spacing = 0.016, ## We calculated this below in standardize_pattern_spacing()
      columns_alignment = c(0, 0, rep(2, 10)),
      columns_width = column_widths_stand$p1, ## This is the column-width object we set above
      columns_table_sig_superscript_letter = "a",
      columns_table_sig_superscript_letter_nudge_x = 5.5,
      columns_nudge_y = c(-0.5, rep(0, 11)),
      headers_alignment = c(0, 0, rep(0.5, 7), 0, 0.5, 0.5, 0),
      headers_row_height = 1.75,
      headers_nudge_x = c(rep(0, 9), 2, rep(0, 3)),
      default_list = abb_6.6
    )
  )



  p_2 <- plot_tablebarplot(
    dat = dat_prepped,
    bar_est = "est_mean_comp_trend_sameFacet_sameSubgroup_2015_2022",
    bar_label = NULL,
    bar_sig = "sig_mean_comp_trend_sameFacet_sameSubgroup_2009_2015",
    bar_fill = "subgroup_var",
    column_spanners = list(
      "**Differenz 2022-2015**" = c(1, 4)
    ),
    headers = list(
      "*M<sub>2022</sub>-<br>M<sub>2015</sub>* ",
      "*(SE)*",
      "*d*",
      " "
    ),
    columns_table = c(
      "est_mean_comp_trend_sameFacet_sameSubgroup_2015_2022",
      "se_mean_comp_trend_sameFacet_sameSubgroup_2015_2022",
      "es_mean_comp_trend_sameFacet_sameSubgroup_2015_2022"
    ),
    columns_table_se = list(NULL, "se_mean_comp_trend_sameFacet_sameSubgroup_2015_2022", NULL),
    columns_table_sig_bold = list("sig_mean_comp_trend_sameFacet_sameSubgroup_2015_2022", NULL, "sig_mean_comp_trend_sameFacet_sameSubgroup_2015_2022"),
    columns_table_sig_superscript = list("sig_mean_comp_trend_crossDiff_totalFacet_sameSubgroup_2015_2022", NULL, NULL),
    y_axis = "y_axis",
    columns_round = c(0, 0, 2),
    plot_settings = plotsettings_tablebarplot(
      axis_x_lims = c(-70, 72),
      bar_pattern_spacing = 0.034, ## We calculated this below in standardize_pattern_spacing()
      columns_alignment = c(2, 2, 2),
      columns_width = column_widths_stand$p2, ## This is the column-width object we set above
      columns_table_sig_superscript_letter = "a",
      columns_table_sig_superscript_letter_nudge_x = 5.5,
      headers_nudge_x = c(2, 0, 0, 0),
      headers_alignment = c(0, 0.5, 0.5, 0),
      headers_row_height = 1.75,
      default_list = abb_6.6
    )
  )

  tableplot_6.6 <- combine_plots(list(p_1, p_2))

  save_plot(tableplot_6.6,
    filename = paste0(
      "C:/Users/hafiznij/Downloads/abb_6.6_",
      unique(dat_prepped$kb),
      ".pdf"
    ),
    width = 235,
    height = 130,
    scaling = 1
  )

  return(tableplot_6.6)
}
```

These function now do the same thing we have done above, but we can easily exchange the data set:

```{r}
#| eval: false
prepped_hoeren <- prepare_6.6_data(kap_06$hoeren)
plot_hoeren <- plot_6.6(prepped_hoeren)
```

## 4. Looping over the competence areas
Now we can use that function for looping over all competence areas with `lapply()`:

```{r}
#| echo: false

plot_6.6 <- function(dat_prepped) {
  column_widths_stand <- standardize_column_width(
    column_widths = list(
      p1 = c(0.085, 0.05, rep(0.035, 6), 0.015, rep(0.035, 3), NA),
      p2 = c(rep(0.035, 3), NA)
    ),
    plot_ranges = c(140, 142) # Ranges of the x-axes of both plots set in 'axis_x_lims'.
  )


  ## 3. Tabellen erzeugen:
  ## Dafür copy-pasten wir einfach von der Vorlage:

  p_1 <- plot_tablebarplot(
    dat = dat_prepped,
    bar_est = "est_mean_comp_trend_sameFacet_sameSubgroup_2009_2015",
    bar_label = NULL,
    bar_sig = "sig_mean_comp_trend_sameFacet_sameSubgroup_2009_2015",
    bar_fill = "subgroup_var",
    column_spanners = list(
      "**2009**" = c(3, 4),
      "**2015**" = c(5, 6),
      "**2022**" = c(7, 8),
      "**Differenz 2015-2009**" = c(10, 13)
    ),
    columns_table_se = list(NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, "se_mean_comp_trend_sameFacet_sameSubgroup_2009_2015", NULL),
    headers = list("**Land**", " ", "*M*", "*SD*", "*M*", "*SD*", "*M*", "*SD*", "", "*M<sub>2015</sub>-<br>M<sub>2009</sub>* ", "*(SE)*", "*d*", " "),
    columns_table = c("state_var", "subgroup_var", "est_mean_comp_none_2009", "est_sd_comp_none_2009", "est_mean_comp_none_2015", "est_sd_comp_none_2015", "est_mean_comp_none_2022", "est_sd_comp_none_2022", "empty", "est_mean_comp_trend_sameFacet_sameSubgroup_2009_2015", "se_mean_comp_trend_sameFacet_sameSubgroup_2009_2015", "es_mean_comp_trend_sameFacet_sameSubgroup_2009_2015"),
    columns_table_sig_bold = list(
      NULL, NULL, "sig_mean_comp_none_2009",
      NULL, "sig_mean_comp_none_2015", NULL, "sig_mean_comp_none_2022", NULL, NULL, "sig_mean_comp_trend_sameFacet_sameSubgroup_2009_2015", NULL, "sig_mean_comp_trend_sameFacet_sameSubgroup_2009_2015"
    ),
    columns_table_sig_superscript = list(NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, "sig_mean_comp_trend_crossDiff_totalFacet_sameSubgroup_2009_2015", NULL, NULL),
    y_axis = "y_axis",
    columns_round = c(rep(0, 11), 2),
    plot_settings = plotsettings_tablebarplot(
      axis_x_lims = c(-70, 70),
      bar_pattern_spacing = 0.016, ## We calculated this below in standardize_pattern_spacing()
      columns_alignment = c(0, 0, rep(2, 10)),
      columns_width = column_widths_stand$p1, ## This is the column-width object we set above
      columns_table_sig_superscript_letter = "a",
      columns_table_sig_superscript_letter_nudge_x = 5.5,
      columns_nudge_y = c(-0.5, rep(0, 11)),
      headers_alignment = c(0, 0, rep(0.5, 7), 0, 0.5, 0.5, 0),
      headers_row_height = 1.75,
      headers_nudge_x = c(rep(0, 9), 2, rep(0, 3)),
      default_list = abb_6.6
    )
  )



  p_2 <- plot_tablebarplot(
    dat = dat_prepped,
    bar_est = "est_mean_comp_trend_sameFacet_sameSubgroup_2015_2022",
    bar_label = NULL,
    bar_sig = "sig_mean_comp_trend_sameFacet_sameSubgroup_2009_2015",
    bar_fill = "subgroup_var",
    column_spanners = list(
      "**Differenz 2022-2015**" = c(1, 4)
    ),
    headers = list(
      "*M<sub>2022</sub>-<br>M<sub>2015</sub>* ",
      "*(SE)*",
      "*d*",
      " "
    ),
    columns_table = c(
      "est_mean_comp_trend_sameFacet_sameSubgroup_2015_2022",
      "se_mean_comp_trend_sameFacet_sameSubgroup_2015_2022",
      "es_mean_comp_trend_sameFacet_sameSubgroup_2015_2022"
    ),
    columns_table_se = list(NULL, "se_mean_comp_trend_sameFacet_sameSubgroup_2015_2022", NULL),
    columns_table_sig_bold = list("sig_mean_comp_trend_sameFacet_sameSubgroup_2015_2022", NULL, "sig_mean_comp_trend_sameFacet_sameSubgroup_2015_2022"),
    columns_table_sig_superscript = list("sig_mean_comp_trend_crossDiff_totalFacet_sameSubgroup_2015_2022", NULL, NULL),
    y_axis = "y_axis",
    columns_round = c(0, 0, 2),
    plot_settings = plotsettings_tablebarplot(
      axis_x_lims = c(-70, 72),
      bar_pattern_spacing = 0.034, ## We calculated this below in standardize_pattern_spacing()
      columns_alignment = c(2, 2, 2),
      columns_width = column_widths_stand$p2, ## This is the column-width object we set above
      columns_table_sig_superscript_letter = "a",
      columns_table_sig_superscript_letter_nudge_x = 5.5,
      headers_nudge_x = c(2, 0, 0, 0),
      headers_alignment = c(0, 0.5, 0.5, 0),
      headers_row_height = 1.75,
      default_list = abb_6.6
    )
  )

  tableplot_6.6 <- combine_plots(list(p_1, p_2))

tableplot_6.6
}


```


```{r}
list_prepped <- lapply(dispar, prepare_6.6_data)
list_plots <- lapply(list_prepped, plot_6.6)
```



