---
title: "Tableplots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tableplots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r echo=FALSE, message = FALSE}
chunkhooks::hook_figure_unit("mm")
```


This vignette shows you how to plot tableplots from `eatRep` data. 
The workflow is optimized for Bildungstrend-graphs, but can be expanded for plotting other `eatRep` data as well. 


```{r}
library(eatPlot)
```

# Geschlechterkapitel
## Abbildung 6.5

First we prepare the data:

```{r}
gender_prepped <- do.call(rbind, lapply(trend_gender, prep_tablebarplot, subgroup_var = "Kgender"))
```

Now, we only want to plot the comparison of male vs. female. 
The direction is always the same, we can look that up in the plain data, therefore it doesn't matter which one we filter:

```{r}
gender_prepped_sub <- subset(gender_prepped, subgroup_var == "male")
```

```{r}
gender_prepped <- gender_prepped_sub[order(gender_prepped_sub$state_var), ]
gender_prepped$y_axis <- 1:nrow(gender_prepped)

gender_prepped$state_var <- process_bundesland(gender_prepped$state_var, linebreak = FALSE)
```

The tables need some more work, because they need to be connected with the barplot, but only have half the rows.
Therefore we need to build separate variables for each table part, with the respective rows of the domain not plotted in the table half set to empty strings. 
Because we want to plot both competence areas next to each other, we have to do some minor data wrangling first:


```{r}
gender_prepped_lesen <- gender_prepped
gender_prepped_lesen[gender_prepped_lesen$kb == "hoeren", !colnames(gender_prepped) %in% c("y_axis", "kb")] <- NA

gender_prepped_hoeren <- gender_prepped
gender_prepped_hoeren[gender_prepped_hoeren$kb == "lesen", !colnames(gender_prepped) %in% c("y_axis", "kb")] <- NA

gender_prepped_lh <- merge(gender_prepped_lesen, gender_prepped_hoeren, by = c("y_axis", "kb"), suffixes = c("_lesen", "_hören"))
gender_prepped_lh_final <- merge(
  gender_prepped_lh,
  gender_prepped[, c(
    "y_axis",
    "est_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022",
    "sig_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022"
  )]
)


gender_prepped_lh_final <- gender_prepped_lh_final[order(gender_prepped_lh_final$y_axis), ]
```



Now we can plot the table like usual, with one exception: I can nudge the table contents a bit downwards, so they also fill the empty row. 


```{r}
tableplot_6.5 <- plot_tablebarplot(
  dat = gender_prepped_lh_final,
  bar_est = "est_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022",
  bar_fill = "kb",
  bar_sig = "sig_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022",
  columns_table = list(
    "state_var_lesen",
    "est_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022_lesen",
    "se_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022_lesen",
    "es_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022_lesen",
    "est_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022_hören",
    "se_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022_hören",
    "es_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022_hören"
  ),
  columns_table_sig_bold = list(
    NULL,
    "sig_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022_lesen",
    NULL,
    "sig_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022_lesen",
    "sig_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022_hören",
    NULL,
    "sig_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022_hören"
  ),
  columns_table_sig_superscript = list(
    NULL,
    "sig_mean_comp_crossDiff_of_groupDiff_totalFacet_femaleSubgroup_2022_lesen",
    NULL,
    "sig_mean_comp_crossDiff_of_groupDiff_totalFacet_femaleSubgroup_2022_lesen",
    "sig_mean_comp_crossDiff_of_groupDiff_totalFacet_femaleSubgroup_2022_hören",
    NULL,
    "sig_mean_comp_crossDiff_of_groupDiff_totalFacet_femaleSubgroup_2022_hören"
  ),
  columns_round = list(NULL, 0, 1, 2, 0, 1, 2),
  columns_table_se = list(
    NULL,
    NULL,
    "se_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022_lesen",
    NULL,
    NULL,
    "se_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022_hören",
    NULL
  ),
  headers = list(
    "**Land**",
    "*M*<sub>M</sub>-*M*<sub>J</sub>",
    "(*SE*)",
    "*d*",
    "*M*<sub>M</sub>-*M*<sub>J</sub>",
    "(*SE*)",
    "*d*",
    "**Vorsprung zugunsten der<br>Mädchen**"
  ),
  column_spanners = list("**Leseverstehen**" = c(2, 4), "**Hörverstehen**" = c(5, 7)),
  y_axis = "y_axis",
  plot_settings = plotsettings_tablebarplot(
    default_list = abb_6.5
  )
)
```

Finally we can save the plot:

```{r}
#| eval: false
save_plot(tableplot_6.5, filename = "C:/Users/hafiznij/Downloads/abb6.5.pdf", width = 160, height = 90)
```

```{r fig.width = 160, fig.height = 90, dpi=300}
tableplot_6.5
```



## Abbildung 6.6

First the data has to be prepared:

```{r}
gender_prepped_mean_sd <- lapply(trend_gender,
  prep_tablebarplot,
  subgroup_var = "Kgender",
  parameter = c("mean", "sd")
)

## Let's focus on:

gender_lesen <- gender_prepped_mean_sd[[1]]
```

Afterwards, we have to bring it in the format we want to plot it in:

```{r}
gender_lesen <- subset(gender_lesen, subgroup_var %in% c("male", "female"))

## females should be the first row always:
gender_lesen <- gender_lesen[order(gender_lesen$subgroup_var), ]
gender_lesen <- gender_lesen[order(gender_lesen$state_var), ]


gender_lesen$state_var <- process_bundesland(gender_lesen$state_var, linebreak = TRUE)
## Depending on whether a column has a linebreak, they have to be nudged down. I define the according vector here already, because it might get confusing furhter down:
nudge_col1_y <- ifelse(grepl("<br>", gender_lesen$state_var), -0.25, -0.5)
  

gender_lesen$state_var[duplicated(gender_lesen$state_var)] <- " "
gender_lesen$subgroup_var <- gsub("^male", "Jungen", gender_lesen$subgroup_var)
gender_lesen$subgroup_var <- gsub("female", "Mädchen", gender_lesen$subgroup_var)
gender_lesen$empty <- ""
```

We will have to plot multiple plots and combine them. 
To do that, we will have to set the column widths, so they are identical over the different plots: 

```{r}
column_widths_stand <- standardize_column_width(
  column_widths = list(
    p1 = c(0.085, 0.05, rep(0.035, 6), 0.015, rep(0.035, 3), NA),
    p2 = c(rep(0.035, 3), NA)
  ),
  plot_ranges = c(142, 142) # Ranges of the x-axes of both plots set in 'axis_x_lims'.
)
```

We can just use this object in the plot-settings to adjust the column widths. 

```{r}


p_1 <- plot_tablebarplot(
  dat = gender_lesen,
  bar_est = "est_mean_comp_trend_sameFacet_sameSubgroup_2009_2015",
  bar_label = NULL,
  bar_sig = "sig_mean_comp_trend_sameFacet_sameSubgroup_2009_2015",
  bar_fill = "subgroup_var",
  column_spanners = list(
    "**2009**" = c(3, 4),
    "**2015**" = c(5, 6),
    "**2022**" = c(7, 8),
    "**Differenz 2015-2009**" = c(10, 13)
  ),
  columns_table_se = list(NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, "se_mean_comp_trend_sameFacet_sameSubgroup_2009_2015", NULL),
  headers = list("**Land**", " ", "*M*", "*SD*", "*M*", "*SD*", "*M*", "*SD*", "", "*M*<sub>2015</sub>-<br>*M*<sub>2009</sub> ", "(*SE*)", "*d*", " "),
  columns_table = c(
    "state_var",
    "subgroup_var",
    "est_mean_comp_none_2009",
    "est_sd_comp_none_2009",
    "est_mean_comp_none_2015",
    "est_sd_comp_none_2015",
    "est_mean_comp_none_2022",
    "est_sd_comp_none_2022",
    "empty",
    "est_mean_comp_trend_sameFacet_sameSubgroup_2009_2015",
    "se_mean_comp_trend_sameFacet_sameSubgroup_2009_2015",
    "es_mean_comp_trend_sameFacet_sameSubgroup_2009_2015"
  ),
  columns_table_sig_bold = list(
    NULL,
    NULL,
    "sig_mean_comp_crossDiff_totalFacet_sameSubgroup_2009",
    NULL,
    "sig_mean_comp_crossDiff_totalFacet_sameSubgroup_2015",
    NULL,
    "sig_mean_comp_crossDiff_totalFacet_sameSubgroup_2022",
    NULL,
    NULL,
    "sig_mean_comp_trend_sameFacet_sameSubgroup_2009_2015",
    NULL,
    "sig_mean_comp_trend_sameFacet_sameSubgroup_2009_2015"
  ),
  columns_table_sig_superscript = list(NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL, "sig_mean_comp_trend_crossDiff_totalFacet_sameSubgroup_2009_2015", NULL, NULL),
  y_axis = "y_axis",
  columns_round = c(rep(0, 10), 1, 2),
  plot_settings = plotsettings_tablebarplot(
    bar_pattern_spacing = 0.01, ## Try out what look good. For own plots, take the template ones as orientation
    columns_alignment = c(0, 0, rep(2, 10)),
    columns_width = column_widths_stand$p1, ## This is the column-width object we set above
    columns_nudge_x = c(rep(0, 9), -1.5, 0, 0),
    columns_nudge_y = c(list(nudge_col1_y), rep(list(0), 11)),
    headers_alignment = c(0, 0, rep(0.5, 7), 0, 0.5, 0.5, 0),
    headers_nudge_x = c(rep(0, 9), 2, rep(0, 3)),
    default_list = abb_6.6
  )
)

p_2 <- plot_tablebarplot(
  dat = gender_lesen,
  bar_est = "est_mean_comp_trend_sameFacet_sameSubgroup_2015_2022",
  bar_label = NULL,
  bar_sig = "sig_mean_comp_trend_sameFacet_sameSubgroup_2015_2022",
  bar_fill = "subgroup_var",
  column_spanners = list(
    "**Differenz 2022-2015**" = c(1, 4)
  ),
  headers = list(
    "*M*<sub>2022</sub>-<br>*M*<sub>2015</sub> ",
    "(*SE*)",
    "*d*",
    " "
  ),
  columns_table = c(
    "est_mean_comp_trend_sameFacet_sameSubgroup_2015_2022",
    "se_mean_comp_trend_sameFacet_sameSubgroup_2015_2022",
    "es_mean_comp_trend_sameFacet_sameSubgroup_2015_2022"
  ),
  columns_table_se = list(NULL, "se_mean_comp_trend_sameFacet_sameSubgroup_2015_2022", NULL),
  columns_table_sig_bold = list("sig_mean_comp_trend_sameFacet_sameSubgroup_2015_2022", 
                                NULL, 
                                "sig_mean_comp_trend_sameFacet_sameSubgroup_2015_2022"),
  columns_table_sig_superscript = list("sig_mean_comp_trend_crossDiff_totalFacet_sameSubgroup_2015_2022", NULL, NULL),
  y_axis = "y_axis",
  columns_round = c(0, 1, 2),
  plot_settings = plotsettings_tablebarplot(
    bar_pattern_spacing = 0.017,
    columns_alignment = c(2, 2, 2),
    columns_width = column_widths_stand$p2, ## This is the column-width object we set above
    headers_nudge_x = c(2, 0, 0, 0),
    headers_alignment = c(0, 0.5, 0.5, 0),
    default_list = abb_6.6
  )
)
``` 


These values have to be set in the plot-settings above.  

Now we can combine the plots:

```{r}
tableplot_6.6 <- combine_plots(list(p_1, p_2))
```

And save the result:
```{r}
#| eval: false

save_plot(tableplot_6.6, filename = "C:/Users/hafiznij/Downloads/abb_6.6.pdf", width = 235, height = 130)
```


```{r fig.width = 235, fig.height = 130, dpi=300}
#| echo: false

tableplot_6.6
```


# Zuwanderungskapitel

Currently use the `gender_trend` data for demonstration purposes, the subgroups are of course named differently for the actual chapter. 

```{r}
gender_prepped_2 <- gender_prepped[gender_prepped$kb == "lesen", ]
gender_prepped_2$empty <- "" ## Needes as a empty space between column spanners
gender_prepped_2$state_var <- process_bundesland(gender_prepped_2$state_var, linebreak = FALSE)
```

```{r}
column_widths_stand <- standardize_column_width(
  column_widths = list(
    p1 = c(0.16, rep(0.045, 5), NA),
    p2 = c(0.015, 0.07, 0.045, NA),
    p3 = c(0.07, 0.045, NA)
  ),
  plot_ranges = c(60, 60, 65) # Range of the x-axes of both plots set in 'axis_x_lims'.
)
```

```{r}
p_1 <- plot_tablebarplot(
  dat = gender_prepped_2,
  bar_est = "est_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022",
  bar_sig = "sig_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022",
  column_spanners = list(
    "**2009**" = c(2),
    "**2015**" = c(3),
    "**2022**" = c(4, 7)
  ),
  column_spanners_2 = list(
    "**Differenz Schüler:innen mit - Schüler:innen ohne <br> Zuwanderungshintergrund**" = c(2, 7)
  ),
  columns_table_se = list(NULL, NULL, NULL, NULL, "se_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022", NULL),
  headers = list(
    "bold(Land)",
    "Delta * italic(M)",
    "Delta * italic(M)",
    "Delta * italic(M)",
    "(italic(SE))",
    "italic(d)",
    " "
  ),
  columns_table = c(
    "state_var",
    "est_mean_comp_groupDiff_sameFacet_femaleSubgroup_2009",
    "est_mean_comp_groupDiff_sameFacet_femaleSubgroup_2015",
    "est_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022",
    "se_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022",
    "es_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022"
  ),
  columns_table_sig_bold = list(
    NULL,
    "sig_mean_comp_groupDiff_sameFacet_femaleSubgroup_2009",
    "sig_mean_comp_groupDiff_sameFacet_femaleSubgroup_2015",
    "sig_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022",
    NULL,
    "sig_mean_comp_groupDiff_sameFacet_femaleSubgroup_2022"
  ),
  columns_round = c(rep(0, 4), 1, 2),
  y_axis = "y_axis",
  plot_settings = plotsettings_tablebarplot(
    bar_pattern_spacing = 0.0274,
    columns_alignment = c(0, 0.5, 0.5, 0.5, 0.5, 0.5),
    columns_width = column_widths_stand$p1,
    default_list = abb_8.4
  )
)
```

```{r}
p_2 <- plot_tablebarplot(
  dat = gender_prepped_2,
  bar_est = "est_mean_comp_trend_groupDiff_sameFacet_femaleSubgroup_2009_2015",
  bar_sig = "sig_mean_comp_trend_groupDiff_sameFacet_femaleSubgroup_2009_2015",
  column_spanners = list(
    "**2015-2009**" = c(2, 4)
  ),
  column_spanners_2 = list(
    "**Veränderung der Differenz<br>**" = c(2, 4)
  ),
  columns_table_se = list(NULL, NULL, "se_mean_comp_trend_groupDiff_sameFacet_femaleSubgroup_2009_2015"),
  headers = list(
    " ",
    list("paste(Delta * italic(M[2015]), '-')",
          "Delta * italic(M[2009])"),
    "(italic(SE))",
    " "
  ),
  columns_table = c(
    "empty",
    "est_mean_comp_trend_groupDiff_sameFacet_femaleSubgroup_2009_2015",
    "se_mean_comp_trend_groupDiff_sameFacet_femaleSubgroup_2009_2015"
  ),
  columns_table_sig_bold = list(
    NULL, "sig_mean_comp_trend_groupDiff_sameFacet_femaleSubgroup_2009_2015", NULL
  ),
  columns_round = c(0, 0, 1), 
  y_axis = "y_axis",
  plot_settings =
    plotsettings_tablebarplot(
      bar_pattern_spacing = 0.0334,
      columns_alignment = c(2, 2, 2),
      headers_alignment = c(0, 0, 0.5, 0),
      headers_nudge_x = c(0, 10, -2, 0),
      columns_width = column_widths_stand$p2,
      default_list = abb_8.4
    )
)
```

```{r}
p_3 <- plot_tablebarplot(
  dat = gender_prepped_2,
  bar_est = "est_mean_comp_trend_groupDiff_sameFacet_femaleSubgroup_2015_2022",
  bar_sig = "sig_mean_comp_trend_groupDiff_sameFacet_femaleSubgroup_2015_2022",
  column_spanners = list(
    "**2022-2015**" = c(1, 3)
  ),
  column_spanners_2 = list(
    "**Veränderung der Differenz<br>**" = c(1, 3)
  ),
  columns_table_se = list(NULL, "se_mean_comp_trend_groupDiff_sameFacet_femaleSubgroup_2015_2022"),
  headers = list(
    list("paste(Delta * italic(M[2022]), '-')",
          "Delta * italic(M[2015])"),
    "(italic(SE))",
    " "
  ),
  columns_table = c(
    "est_mean_comp_trend_groupDiff_sameFacet_femaleSubgroup_2015_2022",
    "se_mean_comp_trend_groupDiff_sameFacet_femaleSubgroup_2015_2022"
  ),
  columns_table_sig_bold = list(
    "sig_mean_comp_trend_groupDiff_sameFacet_femaleSubgroup_2015_2022", NULL
  ),
  columns_round = c(0, 1),
  y_axis = "y_axis",
  plot_settings = plotsettings_tablebarplot(
    bar_pattern_spacing = 0.0392,
    axis_x_lims = c(-20, 45),
    columns_alignment = c(2, 2),
    headers_alignment = c(0, 0.5, 0),
    headers_nudge_x = c(10, -3, 0),
    columns_width = column_widths_stand$p3,
    default_list = abb_8.4
  )
)
```

```{r}
tableplot_8.4 <- combine_plots(list(p_1, p_2, p_3))
```

```{r}
#| eval: false
save_plot(tableplot_8.4,
  filename = "C:/Users/hafiznij/Downloads/abb_8.4.pdf",
  width = 160, height = 100
)
```


```{r fig.width = 160, fig.height = 100, dpi=300}
tableplot_8.4
```

## Stacked Barplot (Abbildung 9.1)
The data preperation for the stacked barplots is  a bit more complicated. 
Most likely, we will have to run at least to analyses with `eatRep`, one for the percentages, and one for the means. 
We prepare both analyses seperately and then merge them:


```{r}
dat_prepped <- prep_tablebarplot(anteile, 
                                 subgroup_var = "Kgender", 
                                   parameter = NULL, 
                                   paramter_to_colname = FALSE)  ## This is important, because our parameter column contains the levels of the dependent Variable. They need to stay in the long format for this one!

dat_prepped_means <- prep_tablebarplot(means, 
                                       subgroup_var = "Kgender", 
                                       parameter = c("mean", "sd"), 
                                       paramter_to_colname = TRUE) ## Here we don't need the long format for the parameters, so we pivot them wider and create parameter specific columns for each comparison! 
  
```

Now I have to do some extra data prep:

```{r}
## Recode subgroup columns
dat_prepped$subgroup_var <- gsub("weiblich", "Mädchen", dat_prepped$subgroup_var)
dat_prepped$subgroup_var <- gsub("maennlich", "Jungen", dat_prepped$subgroup_var)
dat_prepped$subgroup_var <- gsub("total", "Gesamt", dat_prepped$subgroup_var)

## Don't Plot Ncases
dat_prepped <- subset(dat_prepped, parameter != "Ncases")
  
## Make parameter an ordered factor to steer the order of the stacked bars
dat_prepped$parameter <- factor(  dat_prepped$parameter, levels = c("niedrig", "mittel", "hoch"), ordered = TRUE)

## Sort data  
dat_prepped <-   dat_prepped[order(  dat_prepped$subgroup_var), ]
  

## Add an empty row on top
na_row <- as.data.frame(matrix(NA, nrow = 1, ncol = ncol(dat_prepped)))
colnames(na_row) <- colnames(dat_prepped)
dat_prepped <- rbind(na_row, dat_prepped)

## Build bar labels
dat_prepped$label <- paste0(round(dat_prepped$est_NA_comp_none * 100, 0), "%")

## Only plot results for the whole of germany
dat_prepped <- dat_prepped[dat_prepped$state_var == "total", ]

## Fill in the subheader into that empty row. Set to NA for all but the first!
dat_prepped$var <- NA 
dat_prepped[1, "var"] <- "**Allgemeine Schulzufriedenheit**"


## Multiply with 100 to show the perercentages
dat_prepped$est_NA_comp_none <- dat_prepped$est_NA_comp_none * 100


```

This next part is only necessary because my example data does not contain enough subgroups and dependent variable for the actual plot, so I copy paste them onto the data. 
For you, that is not relevent, however, if you have multiple `eatRep`-datasets with different dependent variables, you might need to `rbind()` them together to plot them into one plot. 
I do the same here with my copied data. 

```{r}
## Add additonal subgroups to the data: 
dat_prepped_other_groups <- subset(dat_prepped[-1, ], subgroup_var != "Gesamt")
dat_prepped_other_groups$subgroup_var <- gsub("Jungen","maximal 100 Bücher",  dat_prepped_other_groups$subgroup_var)
dat_prepped_other_groups$subgroup_var <- gsub("Mädchen", "mehr als 100 Bücher", dat_prepped_other_groups$subgroup_var)
dat_prepped_other_groups2 <- subset(dat_prepped[-1, ], subgroup_var != "Gesamt")
dat_prepped_other_groups2$subgroup_var <- gsub( "Jungen", "Zuwanderungshintergrund", dat_prepped_other_groups2$subgroup_var)
dat_prepped_other_groups2$subgroup_var <- gsub( "Mädchen", "ohne Zuwanderungshintergrund", dat_prepped_other_groups2$subgroup_var)

## Because the subgroups are also written into the colnames, I manually rename the columns. 
## Not needed if you actually have different groups in your data. 

colnames(dat_prepped_other_groups) <- gsub("maennlich", "max100books", colnames(dat_prepped_other_groups))
colnames(dat_prepped_other_groups) <- gsub("weiblich", "more100books", colnames(dat_prepped_other_groups))

colnames(dat_prepped_other_groups2) <- gsub("maennlich", "ZWH", colnames(dat_prepped_other_groups2))
colnames(dat_prepped_other_groups2) <- gsub("weiblich", "noZWH", colnames(dat_prepped_other_groups2))

dat_prepped_3 <- dplyr::bind_rows(dat_prepped, dat_prepped_other_groups, dat_prepped_other_groups2)

## Also add values for the y-axis. In tis case it is important that all values, that should be plotted into one row also receive the same values: 
dat_prepped_3$y_axis <- c(8, rep(1, 3), rep(2, 3), rep(3, 3), rep(4, 3), rep(5, 3), rep(6, 3), rep(7, 3))


## Now I can copy this data to simulate other dependent variables
dat_var2 <- dat_prepped_3
dat_var2[1, "var"] <-  "**Soziale Eingebundenheit**"
dat_var2$depVar <- "sozEingeb"
dat_var2$y_axis <- c(16, rep(9, 3), rep(10, 3), rep(11, 3), rep(12, 3), rep(13, 3), rep(14, 3), rep(15, 3))


dat_var3 <- dat_var2
dat_var3[1, "var"] <-  "**Emotionale Probleme**"
dat_var3$depVar <- "emoProb"
dat_var3$y_axis <- c(24, rep(17, 3), rep(18, 3), rep(19, 3), rep(20, 3), rep(21, 3), rep(22, 3), rep(23,3))

dat_var4 <- dat_var3
dat_var4[1, "var"] <-  "**Hyperaktivität**"
dat_var4$depVar <- "hyperAkt"
dat_var4$y_axis <- c(32, rep(25, 3), rep(26, 3), rep(27, 3), rep(28, 3), rep(29,3), rep(30, 3), rep(31,3))



dat <- rbind(dat_prepped_3, dat_var2, dat_var3, dat_var4)


```


```{r}

## Nudging all the rows into the correct position is a bit more complicated here, so I define a vector for it that can be used multiple times: 
nudge_rows <- rep(c(0,  rep(0, 3), rep(-0.125, 3), rep(0.125, 3), rep(-0.125, 3), rep(0.125, 3), rep(-0.125, 3), rep(0.125, 3)), 4)

p_stacked <- plot_tablebarplot(dat,
                    bar_est = "est_NA_comp_none",
                    bar_label = "label",
                    bar_fill = "parameter",
                    columns_table = c("var", "subgroup_var"),
                    headers = c("**Merkmal**", "", ""),
                    y_axis = "y_axis",
                    plot_settings = plotsettings_tablebarplot(
                      bar_fill_colour = c("niedrig" =  "#20D479", "mittel" = "#8DEBBC", "hoch" = "#EBFDF3"),
                      bar_label_colour = c("niedrig" =  "white", "mittel" = "black", "hoch" = "black"),
                      columns_alignment = c(0, 0),
                      columns_width = c(0.1, 0.3, 0.6),
                      bar_label_nudge_x =rep(0.5, nrow(dat)),
                      bar_label_nudge_y = nudge_rows,
                      bar_nudge_y = nudge_rows, 
                      columns_nudge_y = c(list(0), list(nudge_rows)),  
                    default_list = abb_9.1))

```

Now we can prepare the second part of the plot, showing the means. 
We use the prepped means from the separate analysis. 

```{r}
## It is important that the resulting table has the same number of rows as the stacked one.

## First, filter and recode the data as needed
dat_prepped_means <- subset(dat_prepped_means, state_var == "total")
dat_prepped_means$subgroup_var <- gsub("weiblich", "Mädchen", dat_prepped_means$subgroup_var)
dat_prepped_means$subgroup_var <- gsub("maennlich", "Jungen", dat_prepped_means$subgroup_var)
dat_prepped_means$subgroup_var <- gsub("total", "Gesamt", dat_prepped_means$subgroup_var)
dat_prepped_means$subgroup_var <- factor(dat_prepped_means$subgroup_var, levels = c("Gesamt",  "Mädchen",  "Jungen"), ordered = TRUE)

## Again, copy the data to simulate other subgroups, that were not actually in the data!



dat_table_2 <- subset(dat_prepped_means, subgroup_var != "Gesamt")
dat_table_2$subgroup_var <- gsub( "Jungen", "Zuwanderungshintergrund", dat_table_2$subgroup_var)
dat_table_2$subgroup_var <- gsub( "Mädchen", "ohne Zuwanderungshintergrund", dat_table_2$subgroup_var)

dat_table_3 <- subset(dat_prepped_means, subgroup_var != "Gesamt")
dat_table_3$subgroup_var <- gsub("Jungen","maximal 100 Bücher", dat_table_3$subgroup_var)
dat_table_3$subgroup_var <- gsub("Mädchen", "mehr als 100 Bücher", dat_table_3$subgroup_var)


## Because the subgroups are also written into the colnames, I manually rename the columns. 
## Not needed if you actually have different groups in your data. 

dat_table_2$est_mean_comp_groupDiff_sameFacet_more100booksSubgroup_NA

colnames(dat_table_2) <- gsub("maennlich", "max100books", colnames(dat_table_2))
colnames(dat_table_2) <- gsub("weiblich", "more100books", colnames(dat_table_2))

## Manually give them other values, not needed if you have actually different groups
dat_table_2$est_mean_comp_groupDiff_sameFacet_more100booksSubgroup_NA <- ifelse(!is.na(dat_table_2$est_mean_comp_groupDiff_sameFacet_more100booksSubgroup_NA), -0.201, NA)

dat_table_2$se_mean_comp_groupDiff_sameFacet_more100booksSubgroup_NA <- ifelse(!is.na(dat_table_2$se_mean_comp_groupDiff_sameFacet_more100booksSubgroup_NA), 0.02, NA)

dat_table_2$es_mean_comp_groupDiff_sameFacet_more100booksSubgroup_NA <- ifelse(!is.na(dat_table_2$es_mean_comp_groupDiff_sameFacet_more100booksSubgroup_NA), -0.25, NA)

dat_table_2$est_mean_comp_groupDiff_sameFacet_max100booksSubgroup_NA <- ifelse(!is.na(dat_table_2$est_mean_comp_groupDiff_sameFacet_max100booksSubgroup_NA), -0.201, NA)

dat_table_2$se_mean_comp_groupDiff_sameFacet_max100booksSubgroup_NA <- ifelse(!is.na(dat_table_2$se_mean_comp_groupDiff_sameFacet_max100booksSubgroup_NA), 0.02, NA)

dat_table_2$es_mean_comp_groupDiff_sameFacet_max100booksSubgroup_NA <- ifelse(!is.na(dat_table_2$es_mean_comp_groupDiff_sameFacet_max100booksSubgroup_NA), -0.25, NA)


## Same for the other two subgroups
colnames(dat_table_3) <- gsub("maennlich", "ZWH", colnames(dat_table_3))
colnames(dat_table_3) <- gsub("weiblich", "noZWH", colnames(dat_table_3))

dat_table_3$est_mean_comp_groupDiff_sameFacet_noZWHSubgroup_NA <- ifelse(!is.na(dat_table_3$est_mean_comp_groupDiff_sameFacet_noZWHSubgroup_NA), -0.523, NA)

dat_table_3$se_mean_comp_groupDiff_sameFacet_noZWHSubgroup_NA <- ifelse(!is.na(dat_table_3$se_mean_comp_groupDiff_sameFacet_noZWHSubgroup_NA), 0.03, NA)

dat_table_3$es_mean_comp_groupDiff_sameFacet_noZWHSubgroup_NA <- ifelse(!is.na(dat_table_3$es_mean_comp_groupDiff_sameFacet_noZWHSubgroup_NA), -0.256, NA)

dat_table_3$est_mean_comp_groupDiff_sameFacet_ZWHSubgroup_NA <- ifelse(!is.na(dat_table_3$est_mean_comp_groupDiff_sameFacet_ZWHSubgroup_NA), -0.523, NA)

dat_table_3$se_mean_comp_groupDiff_sameFacet_ZWHSubgroup_NA <- ifelse(!is.na(dat_table_3$se_mean_comp_groupDiff_sameFacet_ZWHSubgroup_NA), 0.03, NA)

dat_table_3$es_mean_comp_groupDiff_sameFacet_ZWHSubgroup_NA <- ifelse(!is.na(dat_table_3$es_mean_comp_groupDiff_sameFacet_ZWHSubgroup_NA), -0.256, NA)


dat2 <- dplyr::bind_rows(dat_prepped_means, dat_table_2, dat_table_3)


## Recode the dependent variable to have the same name as in the other data set. Needed for merging.
dat2$depVar <- "Sfskde_kurz_imp_kat"


## I copy the data now to simulate the other dependent variables. 
dat2_var2 <- dat2
dat2_var2$depVar <- "sozEingeb"

dat2_var3 <- dat2_var2
dat2_var3$depVar <- "emoProb"

dat2_var4<- dat2
dat2_var4$depVar <- "hyperAkt"


dat_means <- rbind(dat2, dat2_var2, dat2_var3, dat2_var4)



## The significances and estimates I want to plot are distributed over multiple columns, because they were group-Diffs. 
## I therefore have to pull them together into the same column :




dat_means$est_groupDiff <- merge_cols(dat_means, "est", "groupDiff")
dat_means$sig_groupDiff <- merge_cols(dat_means, "sig", "groupDiff")
dat_means$es_groupDiff <- merge_cols(dat_means, "es", "groupDiff")
dat_means$se_groupDiff <- merge_cols(dat_means, "se", "groupDiff")

## Nochmal überlegen: Macht das jetzt Sinn so? Oder wird da etwas zusammengepackt, was gar nicht zusammen gehört? 
## Mal andere Werte geben und checken, ob das dann noch so stimmt!

## Now we can merge the data with the data that we used in the stacked barplot. 
## By doing this, we can guarantee easily that the position of the values matches the correct rows in the stacked barplot. 
## Using left_join to preserve the order! BaseR merge doesn't deal with the NAs in the best way here. 

## Joinen funktioniert hier noch nicht richtig!
## Auch zu viele Werte noch drin (Jungen & Mädchen!)
## sollte nur noch einer sein!


dat_table <- dat |>
  dplyr::left_join(dat_means[, c("depVar","subgroup_var", "state_var","est_mean_comp_none_NA", "est_sd_comp_none_NA", "est_groupDiff", "se_groupDiff", "es_groupDiff", "sig_groupDiff")])

## remove duplicates
## Now we can reduce the data set, because we can be sure every row receives a value, due to the y-axis column!
dat_table_u <- unique(dat_table[ ,  c("depVar","subgroup_var", "state_var","est_mean_comp_none_NA", "est_sd_comp_none_NA", "est_groupDiff", "se_groupDiff", "es_groupDiff", "sig_groupDiff", "y_axis")])

## Aktuell entstehen durch das zusammenmergen Duplicates in den GroupDiff spalten: 
## Der GroupDiff ist ja für Jungen & Mädchen gleich!
## Daher: In allen Spalten, die jetzt noch "groupDiff" enthalten, duplicates entfernen
dat_table_u <- dat_table_u %>%
  group_by(depVar) %>%
  mutate(across(contains("groupDiff"), ~ ifelse(duplicated(.), NA, .))) %>%
  ungroup()

nudge_rows_short <- rep(c(0, 0, -0.125, 0.125, -0.125, 0.125, -0.125, 0.125), 4)


## Column werden mit der zeit nicht genug genudged. Links passt es noch! 


p_table <- plot_tablebarplot(
  dat_table_u,
  columns_table = c("est_mean_comp_none_NA", "est_sd_comp_none_NA", "est_groupDiff", "se_groupDiff", "es_groupDiff"),
  headers = c("bolditalic(M)", "bolditalic(SD)", "Delta * bolditalic(M)", "(bolditalic(SE))", "bolditalic(d)"),
  columns_round = c(2, 2, 2, 2, 2),
  columns_table_se = list(NULL, NULL, NULL, "se_groupDiff", NULL),
  y_axis = "y_axis",
  columns_table_sig_bold = list(NULL, NULL, 'sig_groupDiff', NULL, 'sig_groupDiff'), 
  plot_settings = plotsettings_tablebarplot(
    columns_alignment = c(0.5, 0.5, 0.5, 0.5, 0.5),
    columns_width = rep(0.2, 5),
    columns_nudge_y = c(list(nudge_rows_short), list(nudge_rows_short), list(-0.5), list(-0.5), list(-0.5)),
    headers_ggtext = FALSE, 
  default_list = abb_9.1))


p_combined <- combine_plots(list(p_stacked, p_table), plot_widths = c(0.7, 0.3))  #+
  #canvas(210, 297.2/4,  units = "mm")

save_plot(p_combined, "C:/Users/hafiznij/Downloads/stacked.pdf",  height = 150, width = 160)

```

