---
title: "Tableplots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tableplots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette shows you how to plot tableplots from `eatRep` data. 
The workflow is optimized for Bildungstrend-graphs, but can be expanded for plotting other `eatRep` data as well. 


# Trend Lesen Deutsch
```{r}
library(eatPlot)
```

In a first step, the data has to be prepared:

```{r}

trend_3_sub <- trend_3

trend_3_sub$plain <- trend_3_sub$plain[trend_3_sub$plain$comparison %in% c("crossDiff", "none", "trend"), ]

dat_prepped <- prep_tablebarplot(trend_3_sub, 
                                 par = c("mean", "sd"), 
                                 facet_var = "TR_BUNDESLAND", 
                                 total_group = "total")

```

This results in a large dataframe, containing a column for each comparisons made in the data:

```{r}
str(dat_prepped)
```

The columns are all named after the same scheme: 

1. First, the column type is shown: `est_` for example contains estimated values, while `sig_` gives us information about the significance, `es_` about the effect size and `se_` about the standard errors of the estimates.
1. This is followed by the year(s) the value is referring to. 
If it is refering to a trend, this is indicated like so: `2015 - 2009`.
1. Then we can see the type of comparison the values in the column are referring to. 
For example, `none` means that no comparison was made, while `trend` indicates that a trend was calculated. 
`crossDiff` shows us a crossDiff and `crossDiffTotal` a crossDiff between some subgroup and an overarching total group (like a state vs. the whole of Germany). 
See [] for a more thorough description of the different comparsions available in `eatRep`. 

I'd suggest to reduce the `data.frame` by selecting the columns needed for the plot in the next step. 
This makes it easier to spot problems in the data. 
For example, I might have gathered either from the data directly, or from a template, that I will need the following columns:

```{r}

table_dat <- dat_prepped[, c("TR_BUNDESLAND",
    "mhg",
    "est_2009_crossDiffTotal_mean",
    "est_2009_none_mean",
    "est_2009_none_sd",
    "est_2015_none_mean",
    "est_2015_none_sd",
    "est_2015 - 2009_trend_mean",
    "sig_2015 - 2009_trend_mean",
    "se_2015 - 2009_trend_mean",
    "es_2015 - 2009_trend_mean"
  )]

```






```{r}
dat_prepped <- filter(dat_prepped, mhg %in% c("aohneZWH", "einET"), !str_detect(TR_BUNDESLAND, "- total"))
dat_prepped <- arrange(dat_prepped, TR_BUNDESLAND)

dat_prepped$TR_BUNDESLAND[duplicated(dat_prepped$TR_BUNDESLAND)] <- " "

column_widths_stand <- standardize_column_width(
  column_widths = list(
    p1 = c(0.05, 0.05, rep(0.05, 7), NA),
    p2 = c(rep(0.05, 7), NA)
  ),
  plot_ranges = c(80, 120) # Range of the x-axes of both plots set in 'axis_x_lims'.
)

p_1 <- plot_tablebar(
  dat = dat_prepped,
  bar_est = "est_2015 - 2009_trend_mean",
  bar_label = NULL,
  bar_sig = "sig_2015 - 2009_trend_mean",
  bar_fill = "mhg",
  column_spanners = list(
    "**2009**<sup>a</sup>" = c(3, 4),
    "**2015**<sup>a</sup>" = c(5, 6),
    "**Differenz 2015-2009<sup>a</sup>**" = c(7, 10)
  ),
  headers = list(
    "**Land**",
    " ",
    "*M*",
    "*SD*",
    "*M*",
    "*SD*",
    "M<sub>2015</sub> - M<sub>2009</sub>",
    "*(SE)*",
    "*d*",
    " "
  ),
  columns_table = c(
    "TR_BUNDESLAND",
    "mhg",
    "est_2009_none_mean",
    "est_2009_none_sd",
    "est_2015_none_mean",
    "est_2015_none_sd",
    "est_2015 - 2009_trend_mean",
    "se_2015 - 2009_trend_mean",
    "es_2015 - 2009_trend_mean"
  ),
  columns_table_sig_bold = list(
    NULL,
    NULL,
    "sig_2009_none_mean",
    NULL, "sig_2015_none_mean",
    NULL,
    "sig_2015 - 2009_trend_mean",
    NULL,
    NULL
  ),
  y_axis = "y_axis",
  plot_settings = plotsettings_tablebarplot(
    axis_x_lims = c(-40, 40),
    background_stripes_colour = c(rep(c("white", "white", "#EBFDF3", "#EBFDF3"), 8), "grey", "grey"),
    bar_fill_colour = c("#20D479", "#8DEBBC"),
    columns_alignment = c(0, 0, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
    columns_width = column_widths_stand$p1,
    headers_alignment = c(0, 0, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0),
    default_list = barplot_table_plot_pattern
  )
)

p_2 <- plot_tablebar(
  dat = dat_prepped,
  bar_est = "est_2022 - 2015_trend_mean",
  bar_label = NULL,
  bar_sig = "sig_2022 - 2015_trend_mean",
  bar_fill = "mhg",
  column_spanners = list(
    "**2015**" = c(1, 2),
    "**2022**" = c(3, 4),
    "**Differenz 2022-2015**" = c(5, 8)
  ),
  headers = list(
    "*M*",
    "*SD*",
    "*M*",
    "*SD*",
    "M<sub>2022</sub> - M<sub>2015</sub>",
    "*(SE)*",
    "*d*",
    " "
  ),
  columns_table = c(
    "est_2015_none_mean",
    "est_2015_none_sd",
    "est_2022_none_mean",
    "est_2022_none_sd",
    "est_2022 - 2015_trend_mean",
    "se_2022 - 2015_trend_mean",
    "es_2022 - 2015_trend_mean"
  ),
  columns_table_se = list(NULL, NULL, NULL, NULL, NULL, "se_2015 - 2009_trend_mean", NULL),
  columns_table_sig_bold = list(
    "sig_2015_none_mean",
    NULL,
    "sig_2022_none_mean",
    NULL,
    "sig_2022 - 2015_trend_mean",
    NULL,
    NULL
  ),
  columns_table_sig_high = list(
    "sig_2015_none_mean",
    NULL,
    "sig_2022_none_mean",
    NULL,
    "sig_2022 - 2015_trend_mean",
    NULL,
    NULL
  ),
  y_axis = "y_axis",
  plot_settings = plotsettings_tablebarplot(
    axis_x_lims = c(-60, 60),
    background_stripes_colour = c(rep(c("white", "white", "#EBFDF3", "#EBFDF3"), 8), "grey", "grey"),
    bar_fill_colour = c("#20D479", "#8DEBBC"),
    columns_alignment = c(0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
    columns_width = column_widths_stand$p2,
    headers_alignment = c(0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0),
    default_list = barplot_table_plot_pattern
  )
)

example_plot <- combine_plots(list(p_1, p_2))
# save_plot(example_plot, filename = "C:/Users/hafiznij/Downloads/test_table.pdf", width = 320)
# save_plot(example_plot, filename = "/home/nick/Downloads/test_table.pdf", width = 320)
```


```{r}
dat_prepped_crossdiff <- prep_tablebarplot(trend_3, par = c("mean", "sd")) %>%
  filter(comparison == "crossDiff_of_groupDiff") %>%
  select(comparison, TR_BUNDESLAND, parameter, year, est, se, es, sig, mhg) %>%
  pivot_wider(names_from = c(year, comparison, parameter), values_from = c(est, se, es, sig)) %>%
  mutate(y_axis = 1:nrow(.)) %>%
  as.data.frame() %>%
  arrange(TR_BUNDESLAND)
```
